### 2022-12-19 paper/article.tex
Deleted refs.bib

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\lstdefinestyle{mystyle}{
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2
}
\lstset{style=mystyle}
\begin{document}

\title{Icon Generation with Conditional Generative Adversarial Networks}

\author{\IEEEauthorblockN{Diogo Medeiros}
\IEEEauthorblockA{\textit{School of Science and Technology} \\
\textit{University of Trás-os-Montes and Alto Douro}\\
Vila Real, Portugal \\
al70633@alunos.utad.pt}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Background}
Why the topic matters.

What is our problem.

How will we solve it.

Related work.

\subsection{Problem}

\subsection{Objective}

\subsection{Related Work}

\section{Methods}

\section{Results}

\section{Discussion}

\section{Conclusions}

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced. \cite{chollet2021deep}

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\bibliographystyle{IEEEtran}
\bibliography{biblio}

\end{document}

### 2022-12-19 ds/dataset.py
no need for download_dataset

@@ -5,7 +5,6 @@ from dataclasses import dataclass
 from typing import Any
 
 import numpy as np
-import requests
 
 
 @dataclass
@@ -53,15 +52,6 @@ class Icons50Dataset:
         else:
             self.__index += 1
             return self[self.__index - 1]
-
-
-def download_dataset(url: str, file_path: str) -> None:
-    """ Download the dataset """
-    if not os.path.exists(file_path):
-        print(f"Downloading dataset from {url} to {file_path}")
-        response = requests.get(url)
-        with open(file_path, "wb") as f:
-            f.write(response.content)
 
 
 def create_dataset(path: str | bytes | os.PathLike) -> Icons50Dataset:

### 2022-12-19 config.py
quick fixes

@@ -22,4 +22,4 @@ class Params:
 class Icons50Config:
     file_path: str
     params: Params
-    optimizer: Optimizer
+    optim: Optimizer

### 2022-12-19 ds/dataset.py

@@ -70,7 +70,6 @@ def create_dataset(path: str | bytes | os.PathLike) -> Icons50Dataset:
     )
 
 
-# print tuple of labels and subtypes
 def print_labels(dataset: Icons50Dataset, filter_label: int | None = None) -> None:
     """ Print the labels and subtypes """
     # Zip the labels and subtypes
@@ -81,7 +80,6 @@ def print_labels(dataset: Icons50Dataset, filter_label: int | None = None) -> No
     types.sort(key=lambda x: (x[0], x[1]))
     # If a label is specified, print only that label
     if filter_label is not None:
-        types = [(label, subtype) for label, subtype in types
-                 if label == filter_label]
+        types = [x for x in types if x[0] == filter_label]
     for label, subtype in types:
         print(f"{label}: {subtype}")

### 2022-12-19 ds/generation.py

@@ -8,7 +8,7 @@ from ds.dataset import Icons50Dataset
 
 
 def generate_real_samples(dataset: Icons50Dataset, n_samples: int) -> tuple[list[np.ndarray], np.ndarray]:
-    """ Select real samples from the ds """
+    """ Select real samples from the dataset """
     # get images and labels
     images = dataset.images
     labels = dataset.labels

### 2022-12-19 main.py

@@ -13,7 +13,7 @@ from models.generator import create_generator
 from models.train import train_gan
 
 cs = ConfigStore.instance()
-cs.store(name="mnist_config", node=Icons50Config)
+cs.store(name="icons50_config", node=Icons50Config)
 
 
 @hydra.main(version_base=None, config_path="config", config_name="config")
@@ -30,8 +30,8 @@ def main(cfg: Icons50Config) -> None:
         image_size=cfg.params.image_size,
         channels=cfg.params.channels,
         n_classes=cfg.params.n_classes,
-        lr=cfg.optimizer.lr,
-        beta_1=cfg.optimizer.beta_1,
+        lr=cfg.optim.lr,
+        beta_1=cfg.optim.beta_1,
     )
 
     # create the generator
@@ -43,8 +43,8 @@ def main(cfg: Icons50Config) -> None:
     # create the gan
     gan_model = create_gan(
         g_model, d_model,
-        lr=cfg.optimizer.lr,
-        beta_1=cfg.optimizer.beta_1
+        lr=cfg.optim.lr,
+        beta_1=cfg.optim.beta_1
     )
     gan_model.summary()
 

### 2022-12-21 config.py
plot history + renaming stuff

@@ -10,7 +10,7 @@ class Optimizer:
 @dataclass
 class Params:
     latent_dim: int
-    n_classes: int
+    num_classes: int
     image_size: int
     channels: int
     epochs: int

### 2022-12-21 ds/dataset.py

@@ -42,7 +42,7 @@ class Icons50Dataset:
     def __len__(self) -> int:
         return len(self.images)
 
-    def __iter__(self) -> Any:
+    def __iter__(self) -> Icons50Dataset:
         return self
 
     def __next__(self) -> tuple[np.ndarray, np.ndarray]:

### 2022-12-21 ds/generation.py

@@ -7,58 +7,58 @@ from keras.models import Model
 from ds.dataset import Icons50Dataset
 
 
-def generate_real_samples(dataset: Icons50Dataset, n_samples: int) -> tuple[list[np.ndarray], np.ndarray]:
+def generate_real_samples(dataset: Icons50Dataset, num_samples: int) -> tuple[list[np.ndarray], np.ndarray]:
     """ Select real samples from the dataset """
     # get images and labels
     images = dataset.images
     labels = dataset.labels
     # choose random instances
-    ix = np.random.randint(0, images.shape[0], n_samples)
+    ix = np.random.randint(0, images.shape[0], num_samples)
     # select images and labels
     x, labels = images[ix], labels[ix]
     # generate class labels
-    y = np.ones((n_samples, 1))
+    y = np.ones((num_samples, 1))
     return [x, labels], y
 
 
-def generate_latent_points(latent_dim: int, n_samples: int, n_classes: int) -> list[np.ndarray]:
+def generate_latent_points(latent_dim: int, num_samples: int, num_classes: int) -> list[np.ndarray]:
     """ Generate points in the latent space as input for the generator """
     # generate points in the latent space
-    x_input = np.random.randn(latent_dim * n_samples)
+    x_input = np.random.randn(latent_dim * num_samples)
     # reshape into a batch of inputs for the network
-    z_input = x_input.reshape(n_samples, latent_dim)
+    z_input = x_input.reshape(num_samples, latent_dim)
     # generate labels
-    labels = np.random.randint(0, n_classes, n_samples)
+    labels = np.random.randint(0, num_classes, num_samples)
     return [z_input, labels]
 
 
-def generate_fake_samples(generator: Model,
-                          latent_dim: int, n_samples: int, n_classes: int) -> tuple[list[np.ndarray], np.ndarray]:
+def generate_fake_samples(generator: Model, latent_dim: int, num_samples: int,
+                          num_classes: int) -> tuple[list[np.ndarray], np.ndarray]:
     """ Generate fake samples using the generator """
     # generate points in latent space
-    z_input, labels_input = generate_latent_points(latent_dim, n_samples, n_classes)
+    z_input, labels_input = generate_latent_points(latent_dim, num_samples, num_classes)
     # predict outputs
     images = generator.predict_on_batch([z_input, labels_input])
     # create class labels
-    y = np.zeros((n_samples, 1))
+    y = np.zeros((num_samples, 1))
[…]

### 2022-12-21 main.py

@@ -1,5 +1,7 @@
 from __future__ import annotations
 
+import os
+
 import hydra
 from hydra.core.config_store import ConfigStore
 from keras.models import load_model
@@ -7,10 +9,9 @@ from keras.models import load_model
 from config import Icons50Config
 from ds.dataset import create_dataset, print_labels
 from ds.generation import generate_images
-from models.discriminator import create_discriminator
-from models.gan import create_gan
-from models.generator import create_generator
-from models.train import train_gan
+from models.cgan import create_cgan, create_generator, create_discriminator
+from models.history import plot_history
+from models.train import train_cgan
 
 cs = ConfigStore.instance()
 cs.store(name="icons50_config", node=Icons50Config)
@@ -18,59 +19,60 @@ cs.store(name="icons50_config", node=Icons50Config)
 
 @hydra.main(version_base=None, config_path="config", config_name="config")
 def main(cfg: Icons50Config) -> None:
+    """ Main function """
+    # suppress TensorFlow INFO messages
+    os.environ['TF_CPP_MIN_LOG_LEVEL'] = '1'
     # Create the dataset
     dataset = create_dataset(cfg.file_path)
-
     # Shuffle the dataset
     if cfg.params.shuffle:
         dataset.shuffle()
-
     # create the discriminator
-    d_model = create_discriminator(
+    discriminator = create_discriminator(
         image_size=cfg.params.image_size,
         channels=cfg.params.channels,
-        n_classes=cfg.params.n_classes,
+        num_classes=cfg.params.num_classes,
         lr=cfg.optim.lr,
         beta_1=cfg.optim.beta_1,
     )
-
+    discriminator.summary()
     # create the generator
-    g_model = create_generator(
+    generator = create_generator(
         latent_dim=cfg.params.latent_dim,
-        n_classes=cfg.params.n_classes,
+        num_classes=cfg.params.num_classes,
     )
-
+    generator.summary()
     # create the gan
-    gan_model = create_gan(
-        g_model, d_model,
+    cgan = create_cgan(
+        generator=generator,
+        discriminator=discriminator,
         lr=cfg.optim.lr,
         beta_1=cfg.optim.beta_1
     )
-    gan_model.summary()
-
+    cgan.summary()
     # train model
-    train_gan(
-        g_model, d_model, gan_model,
+    history = train_cgan(
+        cgan=cgan,
+        generator=generator,
+        discriminator=discriminator,
         dataset=dataset,
[…]

### 2022-12-21 models/cgan.py

@@ -1,0 +1,98 @@
+from keras import Input
+from keras.layers import Concatenate, Dense, Conv2D, LeakyReLU, Embedding, Reshape, Conv2DTranspose, Flatten, Dropout
+from keras.models import Model
+from tensorflow.keras.optimizers import Adam
+
+
+def create_generator(latent_dim: int, num_classes: int) -> Model:
+    """ Create a generator model """
+    # label input
+    in_label = Input(shape=(1,))
+    # embedding for categorical input
+    li = Embedding(num_classes, 50)(in_label)
+    # linear multiplication
+    n_nodes = 8 * 8
+    li = Dense(n_nodes)(li)
+    # reshape to additional channel
+    li = Reshape((8, 8, 1))(li)
+    # image generator input
+    in_lat = Input(shape=(latent_dim,))
+    # foundation for 8x8 image
+    n_nodes = 128 * 8 * 8
+    gen = Dense(n_nodes)(in_lat)
+    gen = LeakyReLU(alpha=0.2)(gen)
+    gen = Reshape((8, 8, 128))(gen)
+    # merge image gen and label input
+    merge = Concatenate()([gen, li])
+    # upsample to 16x16
+    gen = Conv2DTranspose(128, (4, 4), strides=(2, 2), padding='same')(merge)
+    gen = LeakyReLU(alpha=0.2)(gen)
+    # upsample to 32x32
+    gen = Conv2DTranspose(128, (4, 4), strides=(2, 2), padding='same')(gen)
+    gen = LeakyReLU(alpha=0.2)(gen)
+    # output
+    out_layer = Conv2D(3, (8, 8), activation='tanh', padding='same')(gen)
+    # define model
+    model = Model([in_lat, in_label], out_layer, name='generator')
+    return model
+
+
+# define the combined generator and discriminator model, for updating the generator
+def create_discriminator(image_size: int, channels: int, num_classes: int, lr: float, beta_1: float) -> Model:
+    """ Create a discriminator model """
+    # label input
+    in_label = Input(shape=(1,))
+    # embedding for categorical input
+    li = Embedding(num_classes, 50)(in_label)
+    # scale up to image dimensions with linear activation
+    n_nodes = image_size * image_size
+    li = Dense(n_nodes)(li)
+    # reshape to additional channel
+    li = Reshape((image_size, image_size, 1))(li)
+    # image input
+    in_image = Input(shape=(image_size, image_size, channels))
+    # concat label as a channel
+    merge = Concatenate()([in_image, li])
[…]

### 2022-12-21 models/discriminator.py

@@ -1,43 +1,0 @@
-from keras import Input
-from keras.layers import Embedding, Dense, Reshape, Concatenate, Conv2D, LeakyReLU, Flatten, Dropout
-from keras.models import Model
-from tensorflow.keras.optimizers import Adam
-
-
-# define the standalone discriminator model
-def create_discriminator(image_size: int, channels: int, n_classes: int, lr: float, beta_1: float) -> Model:
-    # label input
-    in_label = Input(shape=(1,))
-    # embedding for categorical input
-    li = Embedding(n_classes, 50)(in_label)
-    # scale up to image dimensions with linear activation
-    n_nodes = image_size * image_size
-    li = Dense(n_nodes)(li)
-    # reshape to additional channel
-    li = Reshape((image_size, image_size, 1))(li)
-    # image input
-    in_image = Input(shape=(image_size, image_size, channels))
-    # concat label as a channel
-    merge = Concatenate()([in_image, li])
-    # downsample to 16x16
-    fe = Conv2D(128, (3, 3), strides=(2, 2), padding='same')(merge)
-    fe = LeakyReLU(alpha=0.2)(fe)
-    # downsample to 8x8
-    fe = Conv2D(128, (3, 3), strides=(2, 2), padding='same')(fe)
-    fe = LeakyReLU(alpha=0.2)(fe)
-    # flatten feature maps
-    fe = Flatten()(fe)
-    # dropout layer
-    fe = Dropout(0.4)(fe)
-    # output layer nodes
-    out_layer = Dense(1, activation='sigmoid')(fe)
-    # define model
-    model = Model([in_image, in_label], out_layer)
-    # compile model
-    opt = Adam(learning_rate=lr, beta_1=beta_1)
-    model.compile(
-        loss='binary_crossentropy',
-        optimizer=opt,
-        metrics=['accuracy']
-    )
-    return model

### 2022-12-21 models/gan.py

@@ -1,23 +1,0 @@
-from keras.models import Model
-from tensorflow.keras.optimizers import Adam
-
-
-# define the combined generator and discriminator model, for updating the generator
-def create_gan(g_model: Model, d_model: Model, lr: float, beta_1: float) -> Model:
-    # make weights in the discriminator not trainable
-    d_model.trainable = False
-    # get noise and label inputs from generator model
-    gen_noise, gen_label = g_model.input
-    # get image output from the generator model
-    gen_output = g_model.output
-    # connect image output and label input from generator as inputs to discriminator
-    gan_output = d_model([gen_output, gen_label])
-    # define gan model as taking noise and label and outputting a classification
-    model = Model([gen_noise, gen_label], gan_output)
-    # compile model
-    opt = Adam(learning_rate=lr, beta_1=beta_1)
-    model.compile(
-        loss='binary_crossentropy',
-        optimizer=opt
-    )
-    return model

### 2022-12-21 models/generator.py

@@ -1,35 +1,0 @@
-from keras import Input
-from keras.layers import Concatenate, Dense, Conv2D, LeakyReLU, Embedding, Reshape, Conv2DTranspose
-from keras.models import Model
-
-
-def create_generator(latent_dim: int, n_classes: int) -> Model:
-    # label input
-    in_label = Input(shape=(1,))
-    # embedding for categorical input
-    li = Embedding(n_classes, 50)(in_label)
-    # linear multiplication
-    n_nodes = 8 * 8
-    li = Dense(n_nodes)(li)
-    # reshape to additional channel
-    li = Reshape((8, 8, 1))(li)
-    # image generator input
-    in_lat = Input(shape=(latent_dim,))
-    # foundation for 8x8 image
-    n_nodes = 128 * 8 * 8
-    gen = Dense(n_nodes)(in_lat)
-    gen = LeakyReLU(alpha=0.2)(gen)
-    gen = Reshape((8, 8, 128))(gen)
-    # merge image gen and label input
-    merge = Concatenate()([gen, li])
-    # upsample to 16x16
-    gen = Conv2DTranspose(128, (4, 4), strides=(2, 2), padding='same')(merge)
-    gen = LeakyReLU(alpha=0.2)(gen)
-    # upsample to 32x32
-    gen = Conv2DTranspose(128, (4, 4), strides=(2, 2), padding='same')(gen)
-    gen = LeakyReLU(alpha=0.2)(gen)
-    # output
-    out_layer = Conv2D(3, (8, 8), activation='tanh', padding='same')(gen)
-    # define model
-    model = Model([in_lat, in_label], out_layer)
-    return model

### 2022-12-21 models/history.py

@@ -1,0 +1,31 @@
+from dataclasses import dataclass, field
+
+
+@dataclass
+class History:
+    """ History of training """
+    d_loss: list[float] = field(default_factory=list)
+    d_acc: list[float] = field(default_factory=list)
+    g_loss: list[float] = field(default_factory=list)
+
+    def add(self, d_loss: float, d_acc: float, g_loss: float) -> None:
+        self.d_loss.append(d_loss)
+        self.d_acc.append(d_acc)
+        self.g_loss.append(g_loss)
+
+
+def plot_history(history: History) -> None:
+    """ Plot the history of training """
+    import matplotlib.pyplot as plt
+    # plot loss
+    plt.subplot(2, 1, 1)
+    plt.plot(history.d_loss, label='discriminator')
+    plt.plot(history.g_loss, label='generator')
+    plt.legend()
+    plt.title('Loss')
+    # plot accuracy
+    plt.subplot(2, 1, 2)
+    plt.plot(history.d_acc, label='discriminator')
+    plt.legend()
+    plt.title('Accuracy')
+    plt.show()

### 2022-12-21 models/train.py

@@ -3,62 +3,75 @@ from keras.models import Model
 
 from ds.dataset import Icons50Dataset
 from ds.generation import generate_real_samples, generate_fake_samples, generate_latent_points
+from models.history import History
 
 
-def summarize_performance(i: int, g_model: Model, d_model: Model, dataset: Icons50Dataset, latent_dim: int,
-                          n_batch: int, n_classes: int) -> None:
+def summarize_performance(epoch: int, generator: Model, discriminator: Model, dataset: Icons50Dataset, latent_dim: int,
+                          batch_size: int, num_classes: int) -> None:
     """ Summarize model performance """
     # prepare real samples
-    [X_real, labels_real], y_real = generate_real_samples(dataset, n_batch)
+    [X_real, labels_real], y_real = generate_real_samples(dataset, batch_size)
     # evaluate discriminator on real examples
-    _, acc_real = d_model.evaluate([X_real, labels_real], y_real, verbose=0)
+    _, acc_real = discriminator.evaluate([X_real, labels_real], y_real, verbose=0)
     # prepare fake examples
-    [X_fake, labels], y_fake = generate_fake_samples(g_model, latent_dim, n_batch, n_classes)
+    [X_fake, labels], y_fake = generate_fake_samples(generator, latent_dim, batch_size, num_classes)
     # evaluate discriminator on fake examples
-    _, acc_fake = d_model.evaluate([X_fake, labels], y_fake, verbose=0)
+    _, acc_fake = discriminator.evaluate([X_fake, labels], y_fake, verbose=0)
     # summarize discriminator performance
-    print(f'> Accuracy real: {acc_real:.2%}%, fake: {acc_fake:.2%}%')
-    # save the generator model tile file
-    # noinspection PyUnusedLocal
-    filename = f'cgan_generator_model_{i + 1}.h5'
-    # g_model.save(filename)
+    print(f'> Epoch {epoch + 1}: '
+          f'acc_real={acc_real:.2%}%, '
+          f'acc_fake={acc_fake:.2%}%')
 
 
-def train_gan(g_model: Model, d_model: Model, gan_model: Model, dataset: Icons50Dataset, latent_dim: int, n_epochs: int,
-              n_batch: int, n_classes: int) -> None:
-    """ Train the GAN model """
+def train_cgan(cgan: Model, generator: Model, discriminator: Model, dataset: Icons50Dataset, latent_dim: int,
+               epochs: int, batch_size: int, num_classes: int) -> History:
[…]

### 2022-12-21 main.py
moved config.py to config/

@@ -6,7 +6,7 @@ import hydra
 from hydra.core.config_store import ConfigStore
 from keras.models import load_model
 
-from config import Icons50Config
+from config.config import Icons50Config
 from ds.dataset import create_dataset, print_labels
 from ds.generation import generate_images
 from models.cgan import create_cgan, create_generator, create_discriminator

### 2022-12-21 ds/dataset.py
check for python version

@@ -1,8 +1,8 @@
 from __future__ import annotations
 
 import os
+import sys
 from dataclasses import dataclass
-from typing import Any
 
 import numpy as np
 
@@ -57,7 +57,11 @@ class Icons50Dataset:
 def create_dataset(path: str | bytes | os.PathLike) -> Icons50Dataset:
     """ Create a dataset from a path """
     # Load the icons-50 dataset
-    icons: dict | Any = np.load(path, allow_pickle=True).item()
+    # check if python version is 3.8 or lower
+    if sys.version_info < (3, 9):
+        icons = np.load(path).item()
+    else:
+        icons = np.load(path, allow_pickle=True)
     # Convert the lists to numpy arrays
     icons = {k: np.array(v) for k, v in icons.items()}
     # Create the dataset

### 2022-12-21 ds/dataset.py
missing .item()

@@ -3,6 +3,7 @@ from __future__ import annotations
 import os
 import sys
 from dataclasses import dataclass
+from typing import Any
 
 import numpy as np
 
@@ -57,11 +58,12 @@ class Icons50Dataset:
 def create_dataset(path: str | bytes | os.PathLike) -> Icons50Dataset:
     """ Create a dataset from a path """
     # Load the icons-50 dataset
+    icons: dict | Any
     # check if python version is 3.8 or lower
     if sys.version_info < (3, 9):
         icons = np.load(path).item()
     else:
-        icons = np.load(path, allow_pickle=True)
+        icons = np.load(path, allow_pickle=True).item()
     # Convert the lists to numpy arrays
     icons = {k: np.array(v) for k, v in icons.items()}
     # Create the dataset

### 2022-12-21 ds/dataset.py
create_dataset now reads from pickle file

@@ -1,9 +1,8 @@
 from __future__ import annotations
 
 import os
-import sys
+import pickle
 from dataclasses import dataclass
-from typing import Any
 
 import numpy as np
 
@@ -58,12 +57,8 @@ class Icons50Dataset:
 def create_dataset(path: str | bytes | os.PathLike) -> Icons50Dataset:
     """ Create a dataset from a path """
     # Load the icons-50 dataset
-    icons: dict | Any
-    # check if python version is 3.8 or lower
-    if sys.version_info < (3, 9):
-        icons = np.load(path).item()
-    else:
-        icons = np.load(path, allow_pickle=True).item()
+    with open(path, 'rb') as f:
+        icons = pickle.load(f)
     # Convert the lists to numpy arrays
     icons = {k: np.array(v) for k, v in icons.items()}
     # Create the dataset

### 2022-12-21 ds/generation.py
list -> tuple, type hints

@@ -7,7 +7,7 @@ from keras.models import Model
 from ds.dataset import Icons50Dataset
 
 
-def generate_real_samples(dataset: Icons50Dataset, num_samples: int) -> tuple[list[np.ndarray], np.ndarray]:
+def generate_real_samples(dataset: Icons50Dataset, num_samples: int):
     """ Select real samples from the dataset """
     # get images and labels
     images = dataset.images
@@ -15,33 +15,33 @@ def generate_real_samples(dataset: Icons50Dataset, num_samples: int) -> tuple[li
     # choose random instances
     ix = np.random.randint(0, images.shape[0], num_samples)
     # select images and labels
-    x, labels = images[ix], labels[ix]
+    x: np.ndarray = images[ix]
+    labels: np.ndarray = labels[ix]
     # generate class labels
     y = np.ones((num_samples, 1))
-    return [x, labels], y
+    return (x, labels), y
 
 
-def generate_latent_points(latent_dim: int, num_samples: int, num_classes: int) -> list[np.ndarray]:
+def generate_latent_points(latent_dim: int, num_samples: int, num_classes: int):
     """ Generate points in the latent space as input for the generator """
     # generate points in the latent space
-    x_input = np.random.randn(latent_dim * num_samples)
+    x_input: np.ndarray = np.random.randn(latent_dim * num_samples)
     # reshape into a batch of inputs for the network
-    z_input = x_input.reshape(num_samples, latent_dim)
+    z_input: np.ndarray = x_input.reshape(num_samples, latent_dim)
     # generate labels
-    labels = np.random.randint(0, num_classes, num_samples)
-    return [z_input, labels]
+    labels: np.ndarray = np.random.randint(0, num_classes, num_samples)
+    return z_input, labels
 
 
-def generate_fake_samples(generator: Model, latent_dim: int, num_samples: int,
-                          num_classes: int) -> tuple[list[np.ndarray], np.ndarray]:
+def generate_fake_samples(generator: Model, latent_dim: int, num_samples: int, num_classes: int):
     """ Generate fake samples using the generator """
     # generate points in latent space
     z_input, labels_input = generate_latent_points(latent_dim, num_samples, num_classes)
     # predict outputs
-    images = generator.predict_on_batch([z_input, labels_input])
+    images: np.ndarray = generator.predict_on_batch([z_input, labels_input])
     # create class labels
     y = np.zeros((num_samples, 1))
-    return [images, labels_input], y
[…]

### 2022-12-21 models/train.py

@@ -10,11 +10,11 @@ def summarize_performance(epoch: int, generator: Model, discriminator: Model, da
                           batch_size: int, num_classes: int) -> None:
     """ Summarize model performance """
     # prepare real samples
-    [X_real, labels_real], y_real = generate_real_samples(dataset, batch_size)
+    (X_real, labels_real), y_real = generate_real_samples(dataset, batch_size)
     # evaluate discriminator on real examples
     _, acc_real = discriminator.evaluate([X_real, labels_real], y_real, verbose=0)
     # prepare fake examples
-    [X_fake, labels], y_fake = generate_fake_samples(generator, latent_dim, batch_size, num_classes)
+    (X_fake, labels), y_fake = generate_fake_samples(generator, latent_dim, batch_size, num_classes)
     # evaluate discriminator on fake examples
     _, acc_fake = discriminator.evaluate([X_fake, labels], y_fake, verbose=0)
     # summarize discriminator performance
@@ -41,15 +41,15 @@ def train_cgan(cgan: Model, generator: Model, discriminator: Model, dataset: Ico
         # enumerate batches over the training set
         for j in range(batches_per_epoch):
             # get randomly selected 'real' samples
-            [X_real, labels_real], y_real = generate_real_samples(dataset, half_batch)
+            (X_real, labels_real), y_real = generate_real_samples(dataset, half_batch)
             # update discriminator model weights
             d_loss1, d_acc1 = discriminator.train_on_batch([X_real, labels_real], y_real)
             # generate 'fake' examples
-            [X_fake, labels], y_fake = generate_fake_samples(generator, latent_dim, half_batch, num_classes)
+            (X_fake, labels), y_fake = generate_fake_samples(generator, latent_dim, half_batch, num_classes)
             # update discriminator model weights
             d_loss2, d_acc2 = discriminator.train_on_batch([X_fake, labels], y_fake)
             # prepare points in latent space as input for the generator
-            [z_input, labels_input] = generate_latent_points(latent_dim, batch_size, num_classes)
+            z_input, labels_input = generate_latent_points(latent_dim, batch_size, num_classes)
             # create inverted labels for the fake samples
             y_gan = np.ones((batch_size, 1))
             # update the generator via the discriminator's error

### 2022-12-21 models/history.py
list -> List (python 3.8)

@@ -1,12 +1,13 @@
 from dataclasses import dataclass, field
+from typing import List
 
 
 @dataclass
 class History:
     """ History of training """
-    d_loss: list[float] = field(default_factory=list)
-    d_acc: list[float] = field(default_factory=list)
-    g_loss: list[float] = field(default_factory=list)
+    d_loss: List[float] = field(default_factory=list)
+    d_acc: List[float] = field(default_factory=list)
+    g_loss: List[float] = field(default_factory=list)
 
     def add(self, d_loss: float, d_acc: float, g_loss: float) -> None:
         self.d_loss.append(d_loss)

### 2022-12-21 ds/generation.py
better type hints

@@ -2,7 +2,7 @@ import math
 
 import matplotlib.pyplot as plt
 import numpy as np
-from keras.models import Model
+from keras.models import Functional
 
 from ds.dataset import Icons50Dataset
 
@@ -33,7 +33,7 @@ def generate_latent_points(latent_dim: int, num_samples: int, num_classes: int):
     return z_input, labels
 
 
-def generate_fake_samples(generator: Model, latent_dim: int, num_samples: int, num_classes: int):
+def generate_fake_samples(generator: Functional, latent_dim: int, num_samples: int, num_classes: int):
     """ Generate fake samples using the generator """
     # generate points in latent space
     z_input, labels_input = generate_latent_points(latent_dim, num_samples, num_classes)
@@ -44,7 +44,7 @@ def generate_fake_samples(generator: Model, latent_dim: int, num_samples: int, n
     return (images, labels_input), y
 
 
-def generate_images(generator: Model, label: int, latent_dim: int, num_images: int = 9) -> None:
+def generate_images(generator: Functional, label: int, latent_dim: int, num_images: int = 9) -> None:
     """ Create a plot of generated images given a label """
     # generate points in latent space
     z_input, _ = generate_latent_points(latent_dim, num_images, 1)

### 2022-12-21 main.py

@@ -1,5 +1,3 @@
-from __future__ import annotations
-
 import os
 
 import hydra

### 2022-12-21 models/cgan.py

@@ -1,10 +1,10 @@
 from keras import Input
 from keras.layers import Concatenate, Dense, Conv2D, LeakyReLU, Embedding, Reshape, Conv2DTranspose, Flatten, Dropout
-from keras.models import Model
+from keras.models import Model, Functional
 from tensorflow.keras.optimizers import Adam
 
 
-def create_generator(latent_dim: int, num_classes: int) -> Model:
+def create_generator(latent_dim: int, num_classes: int) -> Functional:
     """ Create a generator model """
     # label input
     in_label = Input(shape=(1,))
@@ -38,7 +38,7 @@ def create_generator(latent_dim: int, num_classes: int) -> Model:
 
 
 # define the combined generator and discriminator model, for updating the generator
-def create_discriminator(image_size: int, channels: int, num_classes: int, lr: float, beta_1: float) -> Model:
+def create_discriminator(image_size: int, channels: int, num_classes: int, lr: float, beta_1: float) -> Functional:
     """ Create a discriminator model """
     # label input
     in_label = Input(shape=(1,))
@@ -77,7 +77,7 @@ def create_discriminator(image_size: int, channels: int, num_classes: int, lr: f
     return model
 
 
-def create_cgan(generator: Model, discriminator: Model, lr: float, beta_1: float) -> Model:
+def create_cgan(generator: Model, discriminator: Model, lr: float, beta_1: float) -> Functional:
     """ Create a cGAN model """
     # make weights in the discriminator not trainable
     discriminator.trainable = False

### 2022-12-21 models/train.py

@@ -1,13 +1,13 @@
 import numpy as np
-from keras.models import Model
+from keras.models import Functional
 
 from ds.dataset import Icons50Dataset
 from ds.generation import generate_real_samples, generate_fake_samples, generate_latent_points
 from models.history import History
 
 
-def summarize_performance(epoch: int, generator: Model, discriminator: Model, dataset: Icons50Dataset, latent_dim: int,
-                          batch_size: int, num_classes: int) -> None:
+def summarize_performance(epoch: int, generator: Functional, discriminator: Functional, dataset: Icons50Dataset,
+                          latent_dim: int, batch_size: int, num_classes: int) -> None:
     """ Summarize model performance """
     # prepare real samples
     (X_real, labels_real), y_real = generate_real_samples(dataset, batch_size)
@@ -23,8 +23,8 @@ def summarize_performance(epoch: int, generator: Model, discriminator: Model, da
           f'acc_fake={acc_fake:.2%}%')
 
 
-def train_cgan(cgan: Model, generator: Model, discriminator: Model, dataset: Icons50Dataset, latent_dim: int,
-               epochs: int, batch_size: int, num_classes: int) -> History:
+def train_cgan(cgan: Functional, generator: Functional, discriminator: Functional, dataset: Icons50Dataset,
+               latent_dim: int, epochs: int, batch_size: int, num_classes: int) -> History:
     """ Train the cGAN model """
     # create history of performance for plotting
     history = History()

### 2022-12-21 models/history.py
plot_history now with separate figures

@@ -19,13 +19,14 @@ def plot_history(history: History) -> None:
     """ Plot the history of training """
     import matplotlib.pyplot as plt
     # plot loss
-    plt.subplot(2, 1, 1)
+    plt.figure(figsize=(10, 5))
     plt.plot(history.d_loss, label='discriminator')
     plt.plot(history.g_loss, label='generator')
     plt.legend()
     plt.title('Loss')
+    plt.show()
     # plot accuracy
-    plt.subplot(2, 1, 2)
+    plt.figure(figsize=(10, 5))
     plt.plot(history.d_acc, label='discriminator')
     plt.legend()
     plt.title('Accuracy')

### 2022-12-21 models/history.py
import fix

@@ -1,6 +1,8 @@
 from dataclasses import dataclass, field
 from typing import List
 
+from matplotlib import pyplot as plt
+
 
 @dataclass
 class History:
@@ -17,7 +19,6 @@ class History:
 
 def plot_history(history: History) -> None:
     """ Plot the history of training """
-    import matplotlib.pyplot as plt
     # plot loss
     plt.figure(figsize=(10, 5))
     plt.plot(history.d_loss, label='discriminator')

### 2022-12-21 config/config.py
new module names + saving models

@@ -21,5 +21,6 @@ class Params:
 @dataclass
 class Icons50Config:
     file_path: str
+    save_path: str
     params: Params
     optim: Optimizer

### 2022-12-21 data/generation.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 from keras.models import Functional
 
-from ds.dataset import Icons50Dataset
+from data.dataset import Icons50Dataset
 
 
 def generate_real_samples(dataset: Icons50Dataset, num_samples: int):

### 2022-12-21 main.py

@@ -5,11 +5,11 @@ from hydra.core.config_store import ConfigStore
 from keras.models import load_model
 
 from config.config import Icons50Config
-from ds.dataset import create_dataset, print_labels
-from ds.generation import generate_images
-from models.cgan import create_cgan, create_generator, create_discriminator
-from models.history import plot_history
-from models.train import train_cgan
+from data.dataset import create_dataset, print_labels
+from data.generation import generate_images
+from model.cgan import create_cgan, create_generator, create_discriminator
+from model.history import plot_history
+from model.train import train_cgan, save_models
 
 cs = ConfigStore.instance()
 cs.store(name="icons50_config", node=Icons50Config)
@@ -61,6 +61,8 @@ def main(cfg: Icons50Config) -> None:
     )
     # plot history
     plot_history(history)
+    # save models
+    save_models(generator, discriminator, cfg.save_path)
     # load saved generator model
     generator = load_model('cgan_generator.h5')
     # Read the label from user input

### 2022-12-21 model/train.py

@@ -1,9 +1,13 @@
+from __future__ import annotations
+
+import os
+
 import numpy as np
 from keras.models import Functional
 
-from ds.dataset import Icons50Dataset
-from ds.generation import generate_real_samples, generate_fake_samples, generate_latent_points
-from models.history import History
+from data.dataset import Icons50Dataset
+from data.generation import generate_real_samples, generate_fake_samples, generate_latent_points
+from model.history import History
 
 
 def summarize_performance(epoch: int, generator: Functional, discriminator: Functional, dataset: Icons50Dataset,
@@ -71,7 +75,12 @@ def train_cgan(cgan: Functional, generator: Functional, discriminator: Functiona
         # evaluate the model performance, sometimes
         if (i + 1) % 10 == 0:
             summarize_performance(i, generator, discriminator, dataset, latent_dim, batch_size, num_classes)
-    # save the generator model
-    generator.save('cgan_generator.h5')
-
     return history
+
+
+def save_models(generator: Functional, discriminator: Functional, cgan: Functional,
+                save_path: str | bytes | os.PathLike) -> None:
+    """ Save the models """
+    generator.save(os.path.join(save_path, "generator.h5"))
+    discriminator.save(os.path.join(save_path, "discriminator.h5"))
+    cgan.save(os.path.join(save_path, "cgan.h5"))

### 2022-12-22 main.py
missing parameter

@@ -62,7 +62,7 @@ def main(cfg: Icons50Config) -> None:
     # plot history
     plot_history(history)
     # save models
-    save_models(generator, discriminator, cfg.save_path)
+    save_models(generator, discriminator, cgan, cfg.save_path)
     # load saved generator model
     generator = load_model('cgan_generator.h5')
     # Read the label from user input

### 2022-12-22 data/dataset.py
dataset summary

@@ -36,6 +36,10 @@ class Icons50Dataset:
         self.styles = self.styles[p]
         self.renditions = self.renditions[p]
 
+    def summary(self) -> None:
+        for label in range(max(self.labels) + 1):
+            print(f"Label {label}: {np.sum(self.labels == label)} images")
+
     def __getitem__(self, index: int) -> tuple[np.ndarray, np.ndarray]:
         return self.images[index], self.labels[index]
 

### 2022-12-22 data/dataset.py
updated summary() now with option for sorting

@@ -36,9 +36,18 @@ class Icons50Dataset:
         self.styles = self.styles[p]
         self.renditions = self.renditions[p]
 
-    def summary(self) -> None:
-        for label in range(max(self.labels) + 1):
-            print(f"Label {label}: {np.sum(self.labels == label)} images")
+    def summary(self, ordered: bool = False) -> None:
+        """ Print a summary of the dataset """
+        details = [(label, np.count_nonzero(self.labels == label))
+                   for label in np.unique(self.labels)]
+        if ordered:
+            details.sort(key=lambda x: x[1], reverse=True)
+        print("Dataset summary:")
+        print(f"Number of images: {len(self)}")
+        print(f"Number of classes: {len(np.unique(self.labels))}")
+        print("Class distribution:")
+        for label, count in details:
+            print(f"Class {label} has {count} images")
 
     def __getitem__(self, index: int) -> tuple[np.ndarray, np.ndarray]:
         return self.images[index], self.labels[index]

### 2022-12-22 data/dataset.py
improved performance

@@ -38,13 +38,13 @@ class Icons50Dataset:
 
     def summary(self, ordered: bool = False) -> None:
         """ Print a summary of the dataset """
-        details = [(label, np.count_nonzero(self.labels == label))
-                   for label in np.unique(self.labels)]
+        labels = np.unique(self.labels)
+        details = [(label, np.count_nonzero(self.labels == label)) for label in labels]
         if ordered:
             details.sort(key=lambda x: x[1], reverse=True)
         print("Dataset summary:")
         print(f"Number of images: {len(self)}")
-        print(f"Number of classes: {len(np.unique(self.labels))}")
+        print(f"Number of classes: {len(labels)}")
         print("Class distribution:")
         for label, count in details:
             print(f"Class {label} has {count} images")

### 2022-12-22 data/dataset.py
summary now prints first_k, if given

@@ -36,12 +36,14 @@ class Icons50Dataset:
         self.styles = self.styles[p]
         self.renditions = self.renditions[p]
 
-    def summary(self, ordered: bool = False) -> None:
+    def summary(self, ordered: bool = False, first_k: int | None = None) -> None:
         """ Print a summary of the dataset """
         labels = np.unique(self.labels)
         details = [(label, np.count_nonzero(self.labels == label)) for label in labels]
         if ordered:
             details.sort(key=lambda x: x[1], reverse=True)
+        if first_k is not None:
+            details = details[:first_k]
         print("Dataset summary:")
         print(f"Number of images: {len(self)}")
         print(f"Number of classes: {len(labels)}")

### 2022-12-22 data/dataset.py
filter dataset.py

@@ -50,6 +50,23 @@ class Icons50Dataset:
         print("Class distribution:")
         for label, count in details:
             print(f"Class {label} has {count} images")
+        print(f"First {first_k} classes represent {sum(x[1] for x in details) / len(self):.2%}% of the dataset")
+
+    def filter(self, most_common: int | None = None) -> Icons50Dataset:
+        """ Filter the dataset by the number of images per class """
+        if most_common is None:
+            return self
+        labels, counts = np.unique(self.labels, return_counts=True)
+        labels = labels[counts.argsort()[::-1]]
+        labels = labels[:most_common]
+        mask = np.isin(self.labels, labels)
+        return Icons50Dataset(
+            images=self.images[mask],
+            labels=self.labels[mask],
+            subtypes=self.subtypes[mask],
+            styles=self.styles[mask],
+            renditions=self.renditions[mask]
+        )
 
     def __getitem__(self, index: int) -> tuple[np.ndarray, np.ndarray]:
         return self.images[index], self.labels[index]

### 2022-12-22 data/dataset.py
changed order of prints

@@ -42,15 +42,15 @@ class Icons50Dataset:
         details = [(label, np.count_nonzero(self.labels == label)) for label in labels]
         if ordered:
             details.sort(key=lambda x: x[1], reverse=True)
-        if first_k is not None:
-            details = details[:first_k]
         print("Dataset summary:")
         print(f"Number of images: {len(self)}")
         print(f"Number of classes: {len(labels)}")
         print("Class distribution:")
+        if first_k is not None:
+            details = details[:first_k]
+            print(f"First {first_k} classes represent {sum(x[1] for x in details) / len(self):.2%}% of the dataset")
         for label, count in details:
             print(f"Class {label} has {count} images")
-        print(f"First {first_k} classes represent {sum(x[1] for x in details) / len(self):.2%}% of the dataset")
 
     def filter(self, most_common: int | None = None) -> Icons50Dataset:
         """ Filter the dataset by the number of images per class """

### 2022-12-22 data/dataset.py
filter() now maps old labels to new labels

@@ -59,13 +59,15 @@ class Icons50Dataset:
         labels, counts = np.unique(self.labels, return_counts=True)
         labels = labels[counts.argsort()[::-1]]
         labels = labels[:most_common]
-        mask = np.isin(self.labels, labels)
+        # map labels to new labels
+        label_map = {label: i for i, label in enumerate(labels)}
+        labels = np.array([label_map.get(label, -1) for label in self.labels])
         return Icons50Dataset(
-            images=self.images[mask],
-            labels=self.labels[mask],
-            subtypes=self.subtypes[mask],
-            styles=self.styles[mask],
-            renditions=self.renditions[mask]
+            images=self.images[labels != -1],
+            labels=labels[labels != -1],
+            subtypes=self.subtypes[labels != -1],
+            styles=self.styles[labels != -1],
+            renditions=self.renditions[labels != -1],
         )
 
     def __getitem__(self, index: int) -> tuple[np.ndarray, np.ndarray]:

### 2022-12-22 main.py

@@ -25,6 +25,8 @@ def main(cfg: Icons50Config) -> None:
     # Shuffle the dataset
     if cfg.params.shuffle:
         dataset.shuffle()
+    # Filter the dataset
+    dataset.filter(most_common=20)
     # create the discriminator
     discriminator = create_discriminator(
         image_size=cfg.params.image_size,

### 2022-12-22 main.py
Updated main.py

@@ -25,8 +25,6 @@ def main(cfg: Icons50Config) -> None:
     # Shuffle the dataset
     if cfg.params.shuffle:
         dataset.shuffle()
-    # Filter the dataset
-    dataset.filter(most_common=20)
     # create the discriminator
     discriminator = create_discriminator(
         image_size=cfg.params.image_size,

### 2022-12-22 data/dataset.py
preprocess()

@@ -23,8 +23,10 @@ class Icons50Dataset:
 
     def __post_init__(self) -> None:
         self.__index = 0
-        self.images = self.images.astype(np.float32)
-        self.images = (self.images - 127.5) / 127.5
+
+    def preprocess(self) -> None:
+        """ Preprocess the dataset """
+        self.images = (self.images.astype(np.float32) - 127.5) / 127.5
         self.images = np.transpose(self.images, (0, 2, 3, 1))
 
     def shuffle(self) -> None:

### 2022-12-22 config/config.py
Models trained with filtered data

@@ -22,5 +22,6 @@ class Params:
 class Icons50Config:
     file_path: str
     save_path: str
+    filt_save_path: str
     params: Params
     optim: Optimizer

### 2022-12-22 main.py

@@ -3,6 +3,7 @@ import os
 import hydra
 from hydra.core.config_store import ConfigStore
 from keras.models import load_model
+from omegaconf import DictConfig
 
 from config.config import Icons50Config
 from data.dataset import create_dataset, print_labels
@@ -22,6 +23,8 @@ def main(cfg: Icons50Config) -> None:
     os.environ['TF_CPP_MIN_LOG_LEVEL'] = '1'
     # Create the dataset
     dataset = create_dataset(cfg.file_path)
+    # Preprocess the dataset
+    dataset.preprocess()
     # Shuffle the dataset
     if cfg.params.shuffle:
         dataset.shuffle()

### 2022-12-23 paper/article.tex
Introduction -> completed

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+This will be the abstract for the following paper.
 \end{abstract}
@@
 
-\section{Background}
-Why the topic matters.
+\section{Introduction}
 
-What is our problem.
+\subsection{Background}
 
-How will we solve it.
+Conditional Generative Adversarial Networks (cGANs) \cite{Mirza2014} are a variant of Generative Adversarial Networks (GANs) that allow the generation of new data samples with specific properties or characteristics.
+They consist of two neural networks: a generator and a discriminator.
+The generator is trained to generate new data samples that are similar to a training set, while the discriminator is trained to distinguish between real and fake data samples.
 
-Related work.
+cGANs introduce an additional input to the generator and discriminator networks, known as the conditioning variable, which allows the model to generate data with specific characteristics or properties.
+This can be useful in a variety of applications, such as image generation, text generation, and speech generation, where the output data needs to have specific attributes or features \cite{Mirza2014}.
+
+For example, in image generation, the conditioning variable may be a label indicating the class of the image to be generated (e.g., a specific type of animal or object), or it may be an attribute of the image (e.g., the presence or absence of a certain color).
 
@@
 
+Given a public dataset, Icons-50 \cite{Icons50, Hendrycks2018}, comprised of icons and their respective labels, we want to be able to generate a new set of sample icons corresponding to a specific label, such as ``clock" or ``airplane".
+
+This could be useful in applications where a large number of icons with specific characteristics are needed, such as in user interface design or graphics design.
+
 \subsection{Objective}
 
+Using cGANs, it is possible to generate icons with specific characteristics or properties, given a public dataset such as Icons-50.
+To do this, the cGAN would be trained on the Icons-50 dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat" or ``bird".
+
 \subsection{Related Work}
+
+In Mirza and Osindero \cite{Mirza2014}, the authors introduce the concept of conditional generative adversarial networks (cGANs), which are a variant of generative adversarial networks (GANs) that allow the generation of new data samples with specific properties or characteristics.
+The cGANs are constructed by feeding the data and the desired characteristics or properties to both the generator and discriminator networks.
+The authors demonstrate the use of cGANs for generating MNIST digits conditioned on class labels and for learning a multi-modal model.
+They also provide examples of using cGANs for image tagging, where the model is able to generate descriptive tags that are not part of the training labels.
+
+In Liu et al.
+\cite{Liu2021SCCGAN:CGAN}, the authors propose a cGAN-based method for repairing damaged fonts based on style.
+They use the content accuracy and style similarity of the repaired font as evaluation indices to assess the accuracy of the restored style.
+The results show that the cGAN-based method is able to repair damaged fonts in a way that is similar to the correct content.
+This method could be useful for restoring damaged fonts in a variety of applications.
+
+In Loey et al.
+\cite{Loey2020AImages}, the authors propose the use of classical data augmentation techniques along with a cGAN based on a deep transfer learning model for COVID-19 detection in chest CT scan images.
+The motivation for this research was the limited availability of benchmark datasets for COVID-19, particularly in chest CT images.
+To address this, the authors collected all available images for COVID-19 and used classical data augmentation techniques along with a cGAN to generate additional images to help in the detection of the virus.
+The results showed that the classical data augmentation techniques along with the cGAN improved the performance of classification in all selected models.
+
+In Ma et al.
+\cite{Ma2018SpeckleCGAN}, the authors propose an end-to-end framework based on a cGAN for simultaneously reducing speckle noise and enhancing contrast in retinal OCT images.
+The cGAN is trained using a novel method for obtaining clean images from outputs of commercial OCT scanners, and an edge loss function is added to the final objective to ensure that the model is sensitive to edge-related details.
+The results show that the proposed method outperforms traditional and other deep learning methods in terms of denoising performance, and has good generalization ability for different types of retinal OCT images.
 
@@
 \section{Conclusions}
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced. \cite{chollet2021deep}
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+Overall, cGANs are an important tool in the field of machine learning, as they allow the generation of data with specific characteristics, which can be useful in a wide range of applications.
 
 \bibliographystyle{IEEEtran}
-\bibliography{biblio}
+\bibliography{paper/references}
 

### 2022-12-23 config/config.py
new SavedModel format + improved config

@@ -19,9 +19,17 @@ class Params:
 
 
 @dataclass
-class Icons50Config:
-    file_path: str
+class Paths:
+    data_path: str
     save_path: str
     filt_save_path: str
+    gen_path: str
+    disc_path: str
+    cgan_path: str
+
+
+@dataclass
+class Icons50Config:
+    paths: Paths
     params: Params
     optim: Optimizer

### 2022-12-23 main.py

@@ -3,7 +3,6 @@ import os
 import hydra
 from hydra.core.config_store import ConfigStore
 from keras.models import load_model
-from omegaconf import DictConfig
 
 from config.config import Icons50Config
 from data.dataset import create_dataset, print_labels
@@ -22,7 +21,7 @@ def main(cfg: Icons50Config) -> None:
     # suppress TensorFlow INFO messages
     os.environ['TF_CPP_MIN_LOG_LEVEL'] = '1'
     # Create the dataset
-    dataset = create_dataset(cfg.file_path)
+    dataset = create_dataset(cfg.paths.data_path)
     # Preprocess the dataset
     dataset.preprocess()
     # Shuffle the dataset
@@ -65,12 +64,22 @@ def main(cfg: Icons50Config) -> None:
     # plot history
     plot_history(history)
     # save models
-    save_models(generator, discriminator, cgan, cfg.save_path)
+    save_models(
+        generator=generator,
+        discriminator=discriminator,
+        cgan=cgan,
+        save_path=cfg.paths.save_path,
+        gen_name=cfg.paths.gen_path,
+        disc_name=cfg.paths.disc_path,
+        cgan_name=cfg.paths.cgan_path
+    )
+    # filter the dataset
+    filtered_ds = dataset.filter(most_common=20)
     # load saved generator model
-    generator = load_model('cgan_generator.h5')
+    generator = load_model(os.path.join(cfg.paths.filt_save_path, cfg.paths.gen_path))
     # Read the label from user input
     label = int(input("Enter the label: "))
-    print_labels(dataset, label)
+    print_labels(filtered_ds, label)
     # generate images
     generate_images(
         generator=generator,

### 2022-12-23 model/train.py

@@ -79,8 +79,8 @@ def train_cgan(cgan: Functional, generator: Functional, discriminator: Functiona
 
 
 def save_models(generator: Functional, discriminator: Functional, cgan: Functional,
-                save_path: str | bytes | os.PathLike) -> None:
+                save_path: str | bytes | os.PathLike, gen_name: str, disc_name: str, cgan_name: str) -> None:
     """ Save the models """
-    generator.save(os.path.join(save_path, "generator.h5"))
-    discriminator.save(os.path.join(save_path, "discriminator.h5"))
-    cgan.save(os.path.join(save_path, "cgan.h5"))
+    generator.save(os.path.join(save_path, gen_name))
+    discriminator.save(os.path.join(save_path, disc_name))
+    cgan.save(os.path.join(save_path, cgan_name))

### 2022-12-23 config/config.py
SavedModel format (now working!!)

@@ -23,9 +23,6 @@ class Paths:
     data_path: str
     save_path: str
     filt_save_path: str
-    gen_path: str
-    disc_path: str
-    cgan_path: str
 
 
 @dataclass

### 2022-12-23 main.py

@@ -7,9 +7,8 @@ from keras.models import load_model
 from config.config import Icons50Config
 from data.dataset import create_dataset, print_labels
 from data.generation import generate_images
-from model.cgan import create_cgan, create_generator, create_discriminator
-from model.history import plot_history
-from model.train import train_cgan, save_models
+from model.cgan import create_discriminator, create_generator, create_cgan
+from model.train import save_models, train_cgan
 
 cs = ConfigStore.instance()
 cs.store(name="icons50_config", node=Icons50Config)
@@ -62,21 +61,18 @@ def main(cfg: Icons50Config) -> None:
         num_classes=cfg.params.num_classes
     )
     # plot history
-    plot_history(history)
+    history.plot()
     # save models
     save_models(
         generator=generator,
         discriminator=discriminator,
         cgan=cgan,
-        save_path=cfg.paths.save_path,
-        gen_name=cfg.paths.gen_path,
-        disc_name=cfg.paths.disc_path,
-        cgan_name=cfg.paths.cgan_path
+        path=cfg.paths.save_path
     )
     # filter the dataset
     filtered_ds = dataset.filter(most_common=20)
     # load saved generator model
-    generator = load_model(os.path.join(cfg.paths.filt_save_path, cfg.paths.gen_path))
+    generator = load_model(os.path.join(cfg.paths.filt_save_path, "generator"))
     # Read the label from user input
     label = int(input("Enter the label: "))
     print_labels(filtered_ds, label)

### 2022-12-23 model/history.py

@@ -12,23 +12,20 @@ class History:
     g_loss: List[float] = field(default_factory=list)
 
     def add(self, d_loss: float, d_acc: float, g_loss: float) -> None:
+        """ Add a new entry to the history """
         self.d_loss.append(d_loss)
         self.d_acc.append(d_acc)
         self.g_loss.append(g_loss)
 
+    def plot(self) -> None:
+        """ Plot the history """
+        plt.plot(self.d_loss, label='discriminator')
+        plt.plot(self.g_loss, label='generator')
+        plt.legend()
+        plt.title('Loss')
+        plt.show()
 
-def plot_history(history: History) -> None:
-    """ Plot the history of training """
-    # plot loss
-    plt.figure(figsize=(10, 5))
-    plt.plot(history.d_loss, label='discriminator')
-    plt.plot(history.g_loss, label='generator')
-    plt.legend()
-    plt.title('Loss')
-    plt.show()
-    # plot accuracy
-    plt.figure(figsize=(10, 5))
-    plt.plot(history.d_acc, label='discriminator')
-    plt.legend()
-    plt.title('Accuracy')
-    plt.show()
+        plt.plot(self.d_acc, label='discriminator')
+        plt.legend()
+        plt.title('Accuracy')
+        plt.show()

### 2022-12-23 model/train.py

@@ -79,8 +79,8 @@ def train_cgan(cgan: Functional, generator: Functional, discriminator: Functiona
 
 
 def save_models(generator: Functional, discriminator: Functional, cgan: Functional,
-                save_path: str | bytes | os.PathLike, gen_name: str, disc_name: str, cgan_name: str) -> None:
-    """ Save the models """
-    generator.save(os.path.join(save_path, gen_name))
-    discriminator.save(os.path.join(save_path, disc_name))
-    cgan.save(os.path.join(save_path, cgan_name))
+                path: str | bytes | os.PathLike) -> None:
+    """ Save the models to file in SavedModel format """
+    generator.save(os.path.join(path, 'generator'))
+    discriminator.save(os.path.join(path, 'discriminator'))
+    cgan.save(os.path.join(path, 'cgan'))

### 2022-12-23 classes.py
Create classes.py

@@ -1,0 +1,52 @@
+classes = [
+    "airplane",
+    "arrow",
+    "ball",
+    "person_biking",
+    "bird",
+    "blade",
+    "boat",
+    "book",
+    "building",
+    "rabbit",
+    "person_doing_cartwheel",
+    "clock",
+    "cloud",
+    "disc",
+    "bottle",
+    "face",
+    "letter",
+    "family",
+    "train",
+    "cat",
+    "flag",
+    "flower",
+    "shoe",
+    "person_golfing",
+    "hands",
+    "hat",
+    "heart",
+    "people_holding_hands",
+    "ideograph",
+    "kiss",
+    "lock",
+    "mailbox",
+    "fish",
+    "medal",
+    "money",
+    "monkey",
+    "moon",
+    "mountain",
+    "digit",
+    "phone",
+    "no_symbol",
+    "star",
+    "person_surfing",
+    "tree",
+    "umbrella",
+    "vehicle",
+    "person_playing_water_polo",
+    "worker",
+    "person_wrestling",
+    "writing",
+]

### 2022-12-23 classes.py
improved print_labels() Classes now available in classes.txt

@@ -1,52 +1,0 @@
-classes = [
-    "airplane",
-    "arrow",
-    "ball",
-    "person_biking",
-    "bird",
-    "blade",
-    "boat",
-    "book",
-    "building",
-    "rabbit",
-    "person_doing_cartwheel",
-    "clock",
-    "cloud",
-    "disc",
-    "bottle",
-    "face",
-    "letter",
-    "family",
-    "train",
-    "cat",
-    "flag",
-    "flower",
-    "shoe",
-    "person_golfing",
-    "hands",
-    "hat",
-    "heart",
-    "people_holding_hands",
-    "ideograph",
-    "kiss",
-    "lock",
-    "mailbox",
-    "fish",
-    "medal",
-    "money",
-    "monkey",
-    "moon",
-    "mountain",
-    "digit",
-    "phone",
-    "no_symbol",
-    "star",
-    "person_surfing",
-    "tree",
-    "umbrella",
-    "vehicle",
-    "person_playing_water_polo",
-    "worker",
-    "person_wrestling",
-    "writing",
-]

### 2022-12-23 config/config.py

@@ -21,6 +21,7 @@ class Params:
 @dataclass
 class Paths:
     data_path: str
+    classes_path: str
     save_path: str
     filt_save_path: str
 

### 2022-12-23 ds/dataset.py

@@ -14,6 +14,8 @@ class Icons50Dataset:
     """ image is a 3D numpy array of shape (32, 32, 3) """
     labels: np.ndarray[int]
     """ label is an integer in [0, 49] that represents the class of the image """
+    classes: np.ndarray[str]
+    """ classes is a list of strings that represent the classes of the dataset """
     subtypes: np.ndarray[str]
     """ subtype is a string that represents the icon subtype """
     styles: np.ndarray[str]
@@ -61,12 +63,14 @@ class Icons50Dataset:
         labels, counts = np.unique(self.labels, return_counts=True)
         labels = labels[counts.argsort()[::-1]]
         labels = labels[:most_common]
+        classes = self.classes[labels]
         # map labels to new labels
         label_map = {label: i for i, label in enumerate(labels)}
         labels = np.array([label_map.get(label, -1) for label in self.labels])
         return Icons50Dataset(
             images=self.images[labels != -1],
             labels=labels[labels != -1],
+            classes=classes,
             subtypes=self.subtypes[labels != -1],
             styles=self.styles[labels != -1],
             renditions=self.renditions[labels != -1],
@@ -90,21 +94,31 @@ class Icons50Dataset:
             return self[self.__index - 1]
 
 
-def create_dataset(path: str | bytes | os.PathLike) -> Icons50Dataset:
+def create_dataset(data_path: str | bytes | os.PathLike, classes_path: str | bytes | os.PathLike) -> Icons50Dataset:
     """ Create a dataset from a path """
     # Load the icons-50 dataset
-    with open(path, 'rb') as f:
+    with open(data_path, 'rb') as f:
         icons = pickle.load(f)
     # Convert the lists to numpy arrays
     icons = {k: np.array(v) for k, v in icons.items()}
+    # Read the classes
+    classes = read_classes(classes_path)
+    classes = np.array(classes)
     # Create the dataset
     return Icons50Dataset(
         images=icons["image"],
         labels=icons["class"],
+        classes=classes,
         subtypes=icons["subtype"],
         styles=icons["style"],
         renditions=icons["rendition"]
     )
+
+
+def read_classes(path: str | bytes | os.PathLike) -> list[str]:
+    """ Read the classes from a file """
+    with open(path, 'r') as f:
+        return [line.strip() for line in f]
 
 
 def print_labels(dataset: Icons50Dataset, filter_label: int | None = None) -> None:
[…]

### 2022-12-23 ds/generation.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 from keras.models import Functional
 
-from data.dataset import Icons50Dataset
+from ds.dataset import Icons50Dataset
 
 
 def generate_real_samples(dataset: Icons50Dataset, num_samples: int):

### 2022-12-23 main.py

@@ -5,8 +5,8 @@ from hydra.core.config_store import ConfigStore
 from keras.models import load_model
 
 from config.config import Icons50Config
-from data.dataset import create_dataset, print_labels
-from data.generation import generate_images
+from ds.dataset import create_dataset, print_labels
+from ds.generation import generate_images
 from model.cgan import create_discriminator, create_generator, create_cgan
 from model.train import save_models, train_cgan
 
@@ -20,7 +20,10 @@ def main(cfg: Icons50Config) -> None:
     # suppress TensorFlow INFO messages
     os.environ['TF_CPP_MIN_LOG_LEVEL'] = '1'
     # Create the dataset
-    dataset = create_dataset(cfg.paths.data_path)
+    dataset = create_dataset(
+        data_path=cfg.paths.data_path,
+        classes_path=cfg.paths.classes_path,
+    )
     # Preprocess the dataset
     dataset.preprocess()
     # Shuffle the dataset
@@ -70,7 +73,7 @@ def main(cfg: Icons50Config) -> None:
         path=cfg.paths.save_path
     )
     # filter the dataset
-    filtered_ds = dataset.filter(most_common=20)
+    filtered_ds = dataset.filter(most_common=10)
     # load saved generator model
     generator = load_model(os.path.join(cfg.paths.filt_save_path, "generator"))
     # Read the label from user input

### 2022-12-23 model/train.py

@@ -5,8 +5,8 @@ import os
 import numpy as np
 from keras.models import Functional
 
-from data.dataset import Icons50Dataset
-from data.generation import generate_real_samples, generate_fake_samples, generate_latent_points
+from ds.dataset import Icons50Dataset
+from ds.generation import generate_real_samples, generate_fake_samples, generate_latent_points
 from model.history import History
 
 

### 2022-12-23 ds/dataset.py
dataset.summary() now plots class distribution

@@ -4,6 +4,7 @@ import os
 import pickle
 from dataclasses import dataclass
 
+import matplotlib.pyplot as plt
 import numpy as np
 
 
@@ -53,8 +54,11 @@ class Icons50Dataset:
         if first_k is not None:
             details = details[:first_k]
             print(f"First {first_k} classes represent {sum(x[1] for x in details) / len(self):.2%}% of the dataset")
-        for label, count in details:
-            print(f"Class {label} has {count} images")
+        # plot histogram of class distribution
+        plt.hist([x[1] for x in details], bins=len(details))
+        plt.xlabel("Class label")
+        plt.ylabel("Number of images")
+        plt.show()
 
     def filter(self, most_common: int | None = None) -> Icons50Dataset:
         """ Filter the dataset by the number of images per class """

### 2022-12-23 ds/dataset.py
minor fixes

@@ -49,7 +49,7 @@ class Icons50Dataset:
             details.sort(key=lambda x: x[1], reverse=True)
         print("Dataset summary:")
         print(f"Number of images: {len(self)}")
-        print(f"Number of classes: {len(labels)}")
+        print(f"Number of classes: {len(self.classes)}")
         print("Class distribution:")
         if first_k is not None:
             details = details[:first_k]

### 2022-12-23 model/history.py

@@ -1,7 +1,7 @@
 from dataclasses import dataclass, field
 from typing import List
 
-from matplotlib import pyplot as plt
+import matplotlib.pyplot as plt
 
 
 @dataclass

### 2022-12-23 ds/dataset.py
quick fix

@@ -55,7 +55,7 @@ class Icons50Dataset:
             details = details[:first_k]
             print(f"First {first_k} classes represent {sum(x[1] for x in details) / len(self):.2%}% of the dataset")
         # plot histogram of class distribution
-        plt.hist([x[1] for x in details], bins=len(details))
+        plt.stairs([x[1] for x in details], [x[0] for x in details])
         plt.xlabel("Class label")
         plt.ylabel("Number of images")
         plt.show()

### 2022-12-23 ds/dataset.py
quick fix

@@ -55,7 +55,7 @@ class Icons50Dataset:
             details = details[:first_k]
             print(f"First {first_k} classes represent {sum(x[1] for x in details) / len(self):.2%}% of the dataset")
         # plot histogram of class distribution
-        plt.stairs([x[1] for x in details], [x[0] for x in details])
+        plt.bar([x[0] for x in details], [x[1] for x in details])
         plt.xlabel("Class label")
         plt.ylabel("Number of images")
         plt.show()

### 2022-12-26 ds/dataset.py
better dataset.summary()

@@ -41,24 +41,22 @@ class Icons50Dataset:
         self.styles = self.styles[p]
         self.renditions = self.renditions[p]
 
-    def summary(self, ordered: bool = False, first_k: int | None = None) -> None:
+    def summary(self, first_k: int | None = None) -> None:
         """ Print a summary of the dataset """
-        labels = np.unique(self.labels)
-        details = [(label, np.count_nonzero(self.labels == label)) for label in labels]
-        if ordered:
-            details.sort(key=lambda x: x[1], reverse=True)
+        no_classes = len(self.classes)
+        counts = [np.count_nonzero(self.labels == i) for i in range(no_classes)]
         print("Dataset summary:")
         print(f"Number of images: {len(self)}")
         print(f"Number of classes: {len(self.classes)}")
         print("Class distribution:")
-        if first_k is not None:
-            details = details[:first_k]
-            print(f"First {first_k} classes represent {sum(x[1] for x in details) / len(self):.2%}% of the dataset")
-        # plot histogram of class distribution
-        plt.bar([x[0] for x in details], [x[1] for x in details])
+        plt.hist(counts, bins=50)
         plt.xlabel("Class label")
         plt.ylabel("Number of images")
         plt.show()
+        if first_k is not None:
+            counts.sort(reverse=True)
+            counts = counts[:first_k]
+            print(f"Top {first_k} classes account for {sum(counts)} images ({sum(counts) / len(self):%}%)")
 
     def filter(self, most_common: int | None = None) -> Icons50Dataset:
         """ Filter the dataset by the number of images per class """

### 2022-12-26 ds/dataset.py
working summary() (bug fix)

@@ -41,22 +41,23 @@ class Icons50Dataset:
         self.styles = self.styles[p]
         self.renditions = self.renditions[p]
 
-    def summary(self, first_k: int | None = None) -> None:
+    def summary(self, top_k: int | None = None) -> None:
         """ Print a summary of the dataset """
+        no_images = len(self)
         no_classes = len(self.classes)
-        counts = [np.count_nonzero(self.labels == i) for i in range(no_classes)]
         print("Dataset summary:")
-        print(f"Number of images: {len(self)}")
-        print(f"Number of classes: {len(self.classes)}")
+        print(f"Number of images: {no_images}")
+        print(f"Number of classes: {no_classes}")
         print("Class distribution:")
-        plt.hist(counts, bins=50)
+        if top_k is not None:
+            _, counts = np.unique(self.labels, return_counts=True)
+            counts = counts[counts.argsort()[::-1]]
+            counts = counts[:top_k]
+            print(f"Top {top_k} classes account for {sum(counts)} images ({sum(counts) / no_images:%}%)")
+        plt.hist(self.labels, bins=no_classes)
         plt.xlabel("Class label")
         plt.ylabel("Number of images")
         plt.show()
-        if first_k is not None:
-            counts.sort(reverse=True)
-            counts = counts[:first_k]
-            print(f"Top {first_k} classes account for {sum(counts)} images ({sum(counts) / len(self):%}%)")
 
     def filter(self, most_common: int | None = None) -> Icons50Dataset:
         """ Filter the dataset by the number of images per class """

### 2022-12-26 main.py

@@ -26,6 +26,8 @@ def main(cfg: Icons50Config) -> None:
     )
     # Preprocess the dataset
     dataset.preprocess()
+    # Show dataset summary
+    dataset.summary()
     # Shuffle the dataset
     if cfg.params.shuffle:
         dataset.shuffle()

### 2022-12-27 ds/dataset.py
- removed unnecessary methods + moved functions to Icons50Dataset class + fixed double '%' print + better variable names for train() function

@@ -24,8 +24,9 @@ class Icons50Dataset:
     renditions: np.ndarray[int]
     """ rendition is an integer in [0, 9] that represents the icon version """
 
-    def __post_init__(self) -> None:
-        self.__index = 0
+    def __len__(self) -> int:
+        """ Return the number of images in the dataset """
+        return len(self.images)
 
     def preprocess(self) -> None:
         """ Preprocess the dataset """
@@ -59,13 +60,15 @@ class Icons50Dataset:
         plt.ylabel("Number of images")
         plt.show()
 
-    def filter(self, most_common: int | None = None) -> Icons50Dataset:
-        """ Filter the dataset by the number of images per class """
-        if most_common is None:
-            return self
+    def filter(self, top_k: int) -> Icons50Dataset:
+        """ Filter the dataset to contain only the top k classes """
+        # Get the top k classes
         labels, counts = np.unique(self.labels, return_counts=True)
+        # Sort the classes by count
         labels = labels[counts.argsort()[::-1]]
-        labels = labels[:most_common]
+        # Get the top k labels
+        labels = labels[:top_k]
+        # Filter the dataset
         classes = self.classes[labels]
         # map labels to new labels
         label_map = {label: i for i, label in enumerate(labels)}
@@ -79,63 +82,39 @@ class Icons50Dataset:
             renditions=self.renditions[labels != -1],
         )
 
-    def __getitem__(self, index: int) -> tuple[np.ndarray, np.ndarray]:
-        return self.images[index], self.labels[index]
+    def print_subtypes(self, label: int | None = None) -> None:
+        """ Print the subtypes of the dataset for a given class """
+        if label is None:
+            for label in range(len(self.classes)):
+                print(f"Class {label}: {self.classes[label]}")
+                self.print_subtypes(label)
+            return
+        subtypes, counts = np.unique(self.subtypes[self.labels == label], return_counts=True)
+        print(f"Subtypes for class {label}: {self.classes[label]}")
+        for subtype, count in zip(subtypes, counts):
+            print(f"{subtype}: {count}")
 
-    def __len__(self) -> int:
-        return len(self.images)
-
-    def __iter__(self) -> Icons50Dataset:
-        return self
-
-    def __next__(self) -> tuple[np.ndarray, np.ndarray]:
-        if self.__index >= len(self):
-            self.__index = 0
-            raise StopIteration
[…]

### 2022-12-27 main.py

@@ -5,7 +5,7 @@ from hydra.core.config_store import ConfigStore
 from keras.models import load_model
 
 from config.config import Icons50Config
-from ds.dataset import create_dataset, print_labels
+from ds.dataset import Icons50Dataset, read_classes
 from ds.generation import generate_images
 from model.cgan import create_discriminator, create_generator, create_cgan
 from model.train import save_models, train_cgan
@@ -19,10 +19,12 @@ def main(cfg: Icons50Config) -> None:
     """ Main function """
     # suppress TensorFlow INFO messages
     os.environ['TF_CPP_MIN_LOG_LEVEL'] = '1'
-    # Create the dataset
-    dataset = create_dataset(
+    # Read classes
+    classes = read_classes(cfg.paths.classes_path)
+    # Load dataset
+    dataset = Icons50Dataset.from_pickle(
         data_path=cfg.paths.data_path,
-        classes_path=cfg.paths.classes_path,
+        classes=classes,
     )
     # Preprocess the dataset
     dataset.preprocess()
@@ -75,12 +77,12 @@ def main(cfg: Icons50Config) -> None:
         path=cfg.paths.save_path
     )
     # filter the dataset
-    filtered_ds = dataset.filter(most_common=10)
+    filtered_ds = dataset.filter(top_k=10)
     # load saved generator model
     generator = load_model(os.path.join(cfg.paths.filt_save_path, "generator"))
     # Read the label from user input
     label = int(input("Enter the label: "))
-    print_labels(filtered_ds, label)
+    filtered_ds.print_subtypes(label)
     # generate images
     generate_images(
         generator=generator,

### 2022-12-27 model/history.py

@@ -1,5 +1,4 @@
 from dataclasses import dataclass, field
-from typing import List
 
 import matplotlib.pyplot as plt
 
@@ -7,9 +6,9 @@ import matplotlib.pyplot as plt
 @dataclass
 class History:
     """ History of training """
-    d_loss: List[float] = field(default_factory=list)
-    d_acc: List[float] = field(default_factory=list)
-    g_loss: List[float] = field(default_factory=list)
+    d_loss: list[float] = field(default_factory=list)
+    d_acc: list[float] = field(default_factory=list)
+    g_loss: list[float] = field(default_factory=list)
 
     def add(self, d_loss: float, d_acc: float, g_loss: float) -> None:
         """ Add a new entry to the history """

### 2022-12-27 model/train.py

@@ -23,8 +23,8 @@ def summarize_performance(epoch: int, generator: Functional, discriminator: Func
     _, acc_fake = discriminator.evaluate([X_fake, labels], y_fake, verbose=0)
     # summarize discriminator performance
     print(f'> Epoch {epoch + 1}: '
-          f'acc_real={acc_real:.2%}%, '
-          f'acc_fake={acc_fake:.2%}%')
+          f'acc_real={acc_real:.2%}, '
+          f'acc_fake={acc_fake:.2%}')
 
 
 def train_cgan(cgan: Functional, generator: Functional, discriminator: Functional, dataset: Icons50Dataset,
@@ -41,9 +41,9 @@ def train_cgan(cgan: Functional, generator: Functional, discriminator: Functiona
     # calculate the size of half a batch of samples
     half_batch = int(batch_size / 2)
     # manually enumerate epochs
-    for i in range(epochs):
+    for epoch in range(epochs):
         # enumerate batches over the training set
-        for j in range(batches_per_epoch):
+        for batch in range(batches_per_epoch):
             # get randomly selected 'real' samples
             (X_real, labels_real), y_real = generate_real_samples(dataset, half_batch)
             # update discriminator model weights
@@ -63,8 +63,8 @@ def train_cgan(cgan: Functional, generator: Functional, discriminator: Functiona
             # calculate the discriminator accuracy
             d_acc = 0.5 * np.add(d_acc1, d_acc2)
             # summarize loss on this batch
-            print(f'\r> Epoch {i + 1}: '
-                  f'Batch {j + 1}/{batches_per_epoch}, '
+            print(f'\r> Epoch {epoch + 1}: '
+                  f'Batch {batch + 1}/{batches_per_epoch}, '
                   f'disc_loss={d_loss:.3f}, '
                   f'disc_acc={d_acc:.3f}, '
                   f'gen_loss={g_loss:.3f}',
@@ -73,8 +73,8 @@ def train_cgan(cgan: Functional, generator: Functional, discriminator: Functiona
         # save metrics to history
         history.add(d_loss, d_acc, g_loss)
         # evaluate the model performance, sometimes
-        if (i + 1) % 10 == 0:
-            summarize_performance(i, generator, discriminator, dataset, latent_dim, batch_size, num_classes)
+        if (epoch + 1) % 10 == 0:
+            summarize_performance(epoch, generator, discriminator, dataset, latent_dim, batch_size, num_classes)
     return history
 
 

### 2022-12-27 model/history.py
fix for python 3.8 compatibility

@@ -1,3 +1,5 @@
+from __future__ import annotations
+
 from dataclasses import dataclass, field
 
 import matplotlib.pyplot as plt

### 2022-12-27 ds/dataset.py
better arg name

@@ -95,10 +95,10 @@ class Icons50Dataset:
             print(f"{subtype}: {count}")
 
     @staticmethod
-    def from_pickle(data_path: str | bytes | os.PathLike, classes: list[str]) -> Icons50Dataset:
+    def from_pickle(path: str | bytes | os.PathLike, classes: list[str]) -> Icons50Dataset:
         """ Create a dataset from a path """
         # Load the icons-50 dataset
-        with open(data_path, 'rb') as f:
+        with open(path, 'rb') as f:
             icons = pickle.load(f)
         # Convert the lists to numpy arrays
         icons = {k: np.array(v) for k, v in icons.items()}

### 2022-12-27 main.py

@@ -23,7 +23,7 @@ def main(cfg: Icons50Config) -> None:
     classes = read_classes(cfg.paths.classes_path)
     # Load dataset
     dataset = Icons50Dataset.from_pickle(
-        data_path=cfg.paths.data_path,
+        path=cfg.paths.data_path,
         classes=classes,
     )
     # Preprocess the dataset

### 2022-12-27 ds/dataset.py
better docstring

@@ -10,19 +10,21 @@ import numpy as np
 
 @dataclass
 class Icons50Dataset:
-    """ The Icons-50 dataset """
+    """ The Icons-50 dataset
+    Attributes:
+        images: NumPy array of shape (no_images, 32, 32, 3) containing the images
+        labels: NumPy array of shape (no_images,) containing the class label for each image
+        classes: NumPy array of shape (no_classes,) containing the class names
+        subtypes: NumPy array of shape (no_images,) containing the subtype of each image
+        styles: NumPy array of shape (no_images,) containing the style of each image
+        renditions: NumPy array of shape (no_images,) containing the version of each image
+    """
     images: np.ndarray[np.ndarray]
-    """ image is a 3D numpy array of shape (32, 32, 3) """
     labels: np.ndarray[int]
-    """ label is an integer in [0, 49] that represents the class of the image """
     classes: np.ndarray[str]
-    """ classes is a list of strings that represent the classes of the dataset """
     subtypes: np.ndarray[str]
-    """ subtype is a string that represents the icon subtype """
     styles: np.ndarray[str]
-    """ style is a string that represents the icon style """
     renditions: np.ndarray[int]
-    """ rendition is an integer in [0, 9] that represents the icon version """
 
     def __len__(self) -> int:
         """ Return the number of images in the dataset """

### 2022-12-27 ds/generation.py
better typing

@@ -1,3 +1,5 @@
+from __future__ import annotations
+
 import math
 
 import matplotlib.pyplot as plt
@@ -6,8 +8,10 @@ from keras.models import Functional
 
 from ds.dataset import Icons50Dataset
 
+NDArrayTuple = tuple[np.ndarray, np.ndarray]
 
-def generate_real_samples(dataset: Icons50Dataset, num_samples: int):
+
+def generate_real_samples(dataset: Icons50Dataset, num_samples: int) -> tuple[NDArrayTuple, np.ndarray]:
     """ Select real samples from the dataset """
     # get images and labels
     images = dataset.images
@@ -22,7 +26,7 @@ def generate_real_samples(dataset: Icons50Dataset, num_samples: int):
     return (x, labels), y
 
 
-def generate_latent_points(latent_dim: int, num_samples: int, num_classes: int):
+def generate_latent_points(latent_dim: int, num_samples: int, num_classes: int) -> NDArrayTuple:
     """ Generate points in the latent space as input for the generator """
     # generate points in the latent space
     x_input: np.ndarray = np.random.randn(latent_dim * num_samples)
@@ -33,7 +37,8 @@ def generate_latent_points(latent_dim: int, num_samples: int, num_classes: int):
     return z_input, labels
 
 
-def generate_fake_samples(generator: Functional, latent_dim: int, num_samples: int, num_classes: int):
+def generate_fake_samples(generator: Functional, latent_dim: int, num_samples: int,
+                          num_classes: int) -> tuple[NDArrayTuple, np.ndarray]:
     """ Generate fake samples using the generator """
     # generate points in latent space
     z_input, labels_input = generate_latent_points(latent_dim, num_samples, num_classes)

### 2022-12-27 paper/article.tex

@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
 \usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{enumitem}
 \usepackage{graphicx}
 \usepackage{listings}
-\usepackage{textcomp}
-\usepackage{url}
+\usepackage[hyphens]{url}
+\usepackage[hidelinks,pdfusetitle]{hyperref}
 \usepackage{xcolor}
+\usepackage{siunitx}
+
+\hypersetup{
+    breaklinks=true,
+    pdfauthor={Diogo Medeiros}
+}
+\urlstyle{same}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \lstdefinestyle{mystyle}{
@@
 \lstset{style=mystyle}
+
 \begin{document}
@@
 }
-
 \maketitle
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+GAN, cGAN, generation, icon, style
 \end{IEEEkeywords}
@@
 \section{Introduction}
-
 \subsection{Background}
-
 Conditional Generative Adversarial Networks (cGANs) \cite{Mirza2014} are a variant of Generative Adversarial Networks (GANs) that allow the generation of new data samples with specific properties or characteristics.
@@
 \subsection{Problem}
-
 Given a public dataset, Icons-50 \cite{Icons50, Hendrycks2018}, comprised of icons and their respective labels, we want to be able to generate a new set of sample icons corresponding to a specific label, such as ``clock" or ``airplane".
@@
 \subsection{Objective}
-
 Using cGANs, it is possible to generate icons with specific characteristics or properties, given a public dataset such as Icons-50.
-To do this, the cGAN would be trained on the Icons-50 dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat" or ``bird".
+To do this, the cGAN would be trained on said dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat" or ``bird".
 
 \subsection{Related Work}
-
 In Mirza and Osindero \cite{Mirza2014}, the authors introduce the concept of conditional generative adversarial networks (cGANs), which are a variant of generative adversarial networks (GANs) that allow the generation of new data samples with specific properties or characteristics.
@@
 The results show that the cGAN-based method is able to repair damaged fonts in a way that is similar to the correct content.
-This method could be useful for restoring damaged fonts in a variety of applications.
 
@@
 
-\section{Methods}
+\section{Materials and Methods}
+
+\subsection{Data}
+To achieve our goal, we opted for the public dataset ``Icons-50" \cite{Icons50}, first introduced in \cite{Hendrycks2018}.
+According to the authors, this dataset was initially designed to test the robustness of classifiers to surface variations in objects.
+The dataset includes both new styles of known objects and unexpected instances of known classes, and the authors propose two methods to improve the surface variation robustness of classifiers.
+
+The Icons-50 dataset consists of 10,000 images belonging to 50 classes of icons (e.g., people, food, activities, places, objects, symbols, etc.) collected from different technology companies and platforms (e.g., Apple, Samsung, Google, Facebook, etc.).
+
+Each class has icons with different styles (e.g., Microsoft's flat vector graphics icon style) and different class subtypes (e.g., 'duck' or 'eagle' subtypes in the 'birds' class) \cite{Icons50}.
+
+To summarize, each entry in the dataset is comprised of the following parameters:
+\begin{itemize}
+    \item image - a 3x32x32 NumPy array corresponding to the RGB icon
+    \item class - an integer between 0 and 49 representing the icon's class
+    \item subtype - a string corresponding to the class subtype, e.g., ``broken\_heart" for the class ``heart" (label 26)
+    \item style - a string corresponding to the icon's source, such as Microsoft or Apple
+    \item rendition - an integer between 0 and 9 representing the icon's version
+\end{itemize}
+
+When analyzing the class distribution, we came to the conclusion that the Icons-50 dataset was considerably unbalanced, as seen in Fig.~\ref{fig:Icons50ClassDist}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/icons50/class_dist.png}
+    \caption{Class distribution of the Icons-50 dataset}
+    \label{fig:Icons50ClassDist}
+\end{figure}
+
+This led to the creation of Icons-10, a subset of Icons-50 containing the top 10 most frequent classes in the dataset, with the old labels mapped to new values between 0 and 9.
+The Icons-10 dataset comprises 4170 images and has a fairly balanced class distribution, seen both in Fig.~\ref{fig:Icons10ClassDist} and in Table~\ref{tab:Icons10Desc}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/icons10/class_dist.png}
+    \caption{Class distribution of the Icons-10 dataset}
+    \label{fig:Icons10ClassDist}
+\end{figure}
+
+\begin{table}[htbp]
+    \centering
+    \caption{Icons-10 Dataset}
+    \begin{tabular}{cccc}
+    \hline
+    \textbf{Class} & \textbf{Old label} & \textbf{New label} & \textbf{No. samples} \\ \hline
+    worker & 47 & 0 & 487  \\ 
+    family & 17 & 1 & 455  \\
+    flag & 20 & 2 & 446  \\
+    face & 15 & 3 & 429  \\
+    hands & 24 & 4 & 429  \\
+    clock & 11 & 5 & 417  \\
+    heart & 26 & 6 & 396  \\
+    arrow & 1 & 7 & 392  \\
+    cat & 19 & 8 & 363  \\
+    ideograph & 28 & 9 & 356 \\ \hline
+    \end{tabular}
+    \label{tab:Icons10Desc}
+\end{table}
+
+\subsection{Methods}
+We opted to adapt an already existing implementation of a cGAN model using the \texttt{keras} library, with the original source code available in \cite{BrownleeCGAN, BrownleeGAN}.
+In the original post, the author chooses to train the model with the MNIST Fashion dataset, which is comprised of gray-level images with 28x28 pixels, far different from the Icons-50 dataset specifications.
+
+In the case of a regular GAN, in Fig.~\ref{fig:GANArch}, the generator takes in the input vector randomly drawn from the latent space and outputs the generated image, which is fed to the discriminator, along side real examples from our dataset, and outputs a classification: whether or not it is real.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/architecture/gan_arch.png}
+    \caption{Architecture of traditional Generative Adversarial Networks (GANs)}
+    \label{fig:GANArch}
+\end{figure}
+
+The main difference between the regular GAN and the cGAN models can be seen in Fig.~\ref{fig:cGANArch}.
+The conditioning variable, in our case, is the icon's class label, which is fed both to the generator when generating a new fake icon, and to the discriminator in order to learn whether or not it belongs to the specific class.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/architecture/cgan_arch.png}
+    \caption{Architecture of Conditional Generative Adversarial Networks (cGANs)}
+    \label{fig:cGANArch}
+\end{figure}
+
+With all this in mind, we built our model, starting with the generator.
+
+As it is clear from Fig.~\ref{fig:GenStruct}, the generator takes in the class label of the icon we want to generate and an input vector drawn randomly from the latent space, with a dimension set at 100.
+It has a total of 1.38M parameters.
+
+In terms of the activation layers, we opted for the leaky RELU with an alpha of 0.2, apart from the output layer with a \textit{tanh} activation.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.4\textwidth]{paper/images/summary/generator.png}
+    \caption{Structure of the generator model}
+    \label{fig:GenStruct}
+\end{figure}
+
+Now for the discriminator, as it is evident from (Fig.~\ref{fig:DiscStruct}), we again chose the leaky RELU function with an alpha of 0.2 for most of the model, apart from the output, which in this case has a \textit{sigmoid} activation, as we are dealing with a binary classification problem.
+
+Since the discriminator is to be trained individually, it must be compiled with a given optimizer, in this case, the Adam optimizer, with a learning rate $LR=\num{2e-4}$ and a $\beta_1=0.5$.
+It has a total of 0.22M parameters.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.4\textwidth]{paper/images/summary/discriminator.png}
+    \caption{Structure of the discriminator model}
+    \label{fig:DiscStruct}
+\end{figure}
+
+Finally, we assemble our cGAN model by taking the generator's output and the input class label and feeding them to the discriminator, as seen in Fig.~\ref{fig:cGANStruct}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/summary/cgan.png}
+    \caption{Structure of the cGAN model}
+    \label{fig:cGANStruct}
+\end{figure}
+
+We chose to train trained two models with identical architectures, first with our original dataset, the Icons-50, and then with the new Icons-10 subset.
+Given the smaller dataset, we picked an appropriate batch size to match its length, seen in Table~\ref{tab:ModelParams}.
+
+\begin{table}[htbp]
+    \centering
+    \caption{Model parameters}
+    \begin{tabular}{ccccc}
+    \hline
+    \textbf{Dataset} & \textbf{Parameters} & \textbf{Epochs} & \textbf{Batch Size} & \textbf{Latent Dim} \\ \hline
+    Icons-50 & 1.6M & 100 & 50 & 100 \\
+    Icons-10 & 1.6M & 100 & 30 & 100 \\ \hline
+    \end{tabular}
+    \label{tab:ModelParams}
+\end{table}
 
@@
 
+After training our model with the Icons-50 dataset for 100 epochs, we were able to achieve a remarkable classification accuracy on the discriminator, seen in Fig.~\ref{fig:Icons50Acc}, with a 94\% accuracy for real images and a 98\% accuracy for generated images.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/icons50/icons50_acc.png}
+    \caption{Discriminator accuracy on the Icons-50 dataset}
+    \label{fig:Icons50Acc}
+\end{figure}
+
+In terms of loss, while the discriminator finished with a satisfactory minimal loss of 0.329, the same could not be said for the generator, as its loss kept increasing as the training went along, finishing at a value of around 2.532, as can be seen in Fig.~\ref{fig:Icons50Loss}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/icons50/icons50_loss.png}
+    \caption{Model loss on the Icons-50 dataset}
+    \label{fig:Icons50Loss}
+\end{figure}
+
+Afterwards, we trained a new model, with the same structure, on the Icons-10 subset, again for 100 epochs.
+When analyzing the discriminator's performance, it seemed that both its loss and accuracy suffered.
+
+While the loss only increased slightly, to an acceptable value of 0.643, the accuracy while classifying images as real or fake varied quite drastically during training, as can be seen on Fig.~\ref{fig:Icons10Acc}, finishing at, respectively, 83.33\% and 86.67\%.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/icons10/icons10_acc.png}
+    \caption{Discriminator accuracy on the Icons-10 dataset}
+    \label{fig:Icons10Acc}
+\end{figure}
+
+In terms of the generator's performance, while the loss still varied quite significantly, the the new dataset proved successful, with the model finishing with a much better loss of 1.433, as seen on Fig.~\ref{fig:Icons10Loss}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.48\textwidth]{paper/images/icons10/icons10_loss.png}
+    \caption{Model loss on the Icons-10 dataset}
+    \label{fig:Icons10Loss}
+\end{figure}
+
 \section{Discussion}
+
+ Possibly due to the large number of classes, the model seemed to overfit the data (Icons-50) and the generator loss kept increasing as the training continued, finishing with a not so great loss.
 

### 2022-12-28 ds/generation.py
compat with 3.8

@@ -1,6 +1,7 @@
 from __future__ import annotations
 
 import math
+import sys
 
 import matplotlib.pyplot as plt
 import numpy as np
@@ -8,7 +9,12 @@ from keras.models import Functional
 
 from ds.dataset import Icons50Dataset
 
-NDArrayTuple = tuple[np.ndarray, np.ndarray]
+if sys.version_info >= (3, 9):
+    NDArrayTuple = tuple[np.ndarray, np.ndarray]
+else:
+    from typing import Tuple
+
+    NDArrayTuple = Tuple[np.ndarray, np.ndarray]
 
 
 def generate_real_samples(dataset: Icons50Dataset, num_samples: int) -> tuple[NDArrayTuple, np.ndarray]:

### 2022-12-28 ds/dataset.py
print_classes()

@@ -84,6 +84,11 @@ class Icons50Dataset:
             renditions=self.renditions[labels != -1],
         )
 
+    def print_classes(self) -> None:
+        """ Print the classes of the dataset """
+        for label in range(len(self.classes)):
+            print(f"{label}: {self.classes[label]}")
+
     def print_subtypes(self, label: int | None = None) -> None:
         """ Print the subtypes of the dataset for a given class """
         if label is None:

### 2022-12-28 ds/dataset.py
read_label()

@@ -121,6 +121,18 @@ class Icons50Dataset:
         )
 
 
+def read_label(num_classes: int) -> int:
+    """ Read a label from the user """
+    while True:
+        try:
+            label = int(input("Enter a class label: "))
+            if 0 <= label < num_classes:
+                return label
+            print(f"Invalid class label! Label must be between 0 and {num_classes - 1}")
+        except ValueError:
+            print("Invalid class label! Label must be an integer")
+
+
 def read_classes(path: str | bytes | os.PathLike) -> list[str]:
     """ Read the classes from a file """
     with open(path, 'r') as f:

### 2022-12-28 main.py

@@ -5,7 +5,7 @@ from hydra.core.config_store import ConfigStore
 from keras.models import load_model
 
 from config.config import Icons50Config
-from ds.dataset import Icons50Dataset, read_classes
+from ds.dataset import Icons50Dataset, read_classes, read_label
 from ds.generation import generate_images
 from model.cgan import create_discriminator, create_generator, create_cgan
 from model.train import save_models, train_cgan
@@ -81,7 +81,7 @@ def main(cfg: Icons50Config) -> None:
     # load saved generator model
     generator = load_model(os.path.join(cfg.paths.filt_save_path, "generator"))
     # Read the label from user input
-    label = int(input("Enter the label: "))
+    label = read_label(num_classes=cfg.params.num_classes)
     filtered_ds.print_subtypes(label)
     # generate images
     generate_images(

### 2022-12-28 main.py
load_model()

@@ -2,13 +2,12 @@ import os
 
 import hydra
 from hydra.core.config_store import ConfigStore
-from keras.models import load_model
 
 from config.config import Icons50Config
 from ds.dataset import Icons50Dataset, read_classes, read_label
 from ds.generation import generate_images
 from model.cgan import create_discriminator, create_generator, create_cgan
-from model.train import save_models, train_cgan
+from model.train import save_models, train_cgan, load_generator
 
 cs = ConfigStore.instance()
 cs.store(name="icons50_config", node=Icons50Config)
@@ -79,7 +78,7 @@ def main(cfg: Icons50Config) -> None:
     # filter the dataset
     filtered_ds = dataset.filter(top_k=10)
     # load saved generator model
-    generator = load_model(os.path.join(cfg.paths.filt_save_path, "generator"))
+    generator = load_generator(path=cfg.paths.filt_save_path)
     # Read the label from user input
     label = read_label(num_classes=cfg.params.num_classes)
     filtered_ds.print_subtypes(label)

### 2022-12-28 model/train.py

@@ -3,7 +3,7 @@ from __future__ import annotations
 import os
 
 import numpy as np
-from keras.models import Functional
+from keras.models import Functional, load_model
 
 from ds.dataset import Icons50Dataset
 from ds.generation import generate_real_samples, generate_fake_samples, generate_latent_points
@@ -84,3 +84,9 @@ def save_models(generator: Functional, discriminator: Functional, cgan: Function
     generator.save(os.path.join(path, 'generator'))
     discriminator.save(os.path.join(path, 'discriminator'))
     cgan.save(os.path.join(path, 'cgan'))
+
+
+def load_generator(path: str | bytes | os.PathLike) -> Functional:
+    """ Load the generator model from file """
+    path = os.path.join(path, 'generator')
+    return load_model(path)

### 2023-01-04 paper/article.tex

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage{listings}
@@
 
+To better evaluate the performance of the trained generators, we generated a new set of icons belonging to the classes common to both datasets.
+
+\begin{figure}[htbp]
+    \begin{subfigure}[h]{0.4\linewidth}
+        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons50_clock.png}
+        \caption{Icons-50 dataset}
+        \label{fig:Icons50Clock}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[h]{0.4\linewidth}
+        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons10_clock.png}
+        \caption{Icons-10 dataset}
+        \label{fig:Icons10Clock}
+    \end{subfigure}
+    \caption{Generated icons belonging to class ``clock"}
+    \label{fig:ClockIcons}
+\end{figure}
+
+When given a simple task, such as generating a ``clock" icon, the model trained on the Icons-50 dataset only seemed to perceive the shape of the clock, with none of the defining details being present in the generated images, evident from Fig.~\ref{fig:Icons50Clock}.
+
+The second model performed much better on this task, capturing finer details such as the correct color, and the hour and minutes hands, as it is clear from Fig.~\ref{fig:Icons10Clock}.
+
+\begin{figure}[htbp]
+    \begin{subfigure}[h]{0.4\linewidth}
+        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons50_family.png}
+        \caption{Icons-50 dataset}
+        \label{fig:Icons50Family}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[h]{0.4\linewidth}
+        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons10_family.png}
+        \caption{Icons-10 dataset}
+        \label{fig:Icons10Family}
+    \end{subfigure}
+    \caption{Generated icons belonging to class ``family"}
+    \label{fig:FamilyIcons}
+\end{figure}
+
+When dealing with a complex task, such as generating icons for the ``family" class, the original generator was able to create recognizable images, even though they lacked definition and variability, as seen on Fig.~\ref{fig:Icons50Family}.
+
+When trained on the Icons-10 dataset, the model was able to generate a unique and slightly more detailed set of icons, albeit with variable results, as seen on Fig.~\ref{fig:Icons10Family}.
+
 \section{Discussion}

### 2023-01-05 paper/article.tex
Paper -> finished

@@
 \begin{abstract}
-This will be the abstract for the following paper.
+Conditional Generative Adversarial Networks (cGANs) were used to generate icons with specific characteristics or properties given the Icons-50 dataset.
+The performance of the cGANs was impacted by the imbalanced nature of the original dataset.
+Filtering the original dataset to include only the 10 most frequent classes (the Icons-10 dataset) improved the performance of the cGANs, allowing them to generate more detailed and striking icons.
+This paper demonstrates the potential of cGANs for use in applications where a large number of icons with specific characteristics are needed.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-GAN, cGAN, generation, icon, style
+GAN, cGAN, Icons-50, icons, style, applications
 \end{IEEEkeywords}
@@
 \subsection{Problem}
-Given a public dataset, Icons-50 \cite{Icons50, Hendrycks2018}, comprised of icons and their respective labels, we want to be able to generate a new set of sample icons corresponding to a specific label, such as ``clock" or ``airplane".
+Given a public dataset, Icons-50 \cite{Icons50, Hendrycks2018}, comprised of icons and their respective labels, I want to be able to generate a new set of sample icons corresponding to a specific label, such as ``clock" or ``airplane".
 
@@
 \subsection{Data}
-To achieve our goal, we opted for the public dataset ``Icons-50" \cite{Icons50}, first introduced in \cite{Hendrycks2018}.
+To achieve my goal, I opted for the public dataset ``Icons-50" \cite{Icons50}, first introduced in \cite{Hendrycks2018}.
 According to the authors, this dataset was initially designed to test the robustness of classifiers to surface variations in objects.
@@
 
-Each class has icons with different styles (e.g., Microsoft's flat vector graphics icon style) and different class subtypes (e.g., 'duck' or 'eagle' subtypes in the 'birds' class) \cite{Icons50}.
+Each class has icons with different styles (e.g., Microsoft's flat vector graphics icon style) and different class sub-types (e.g., 'duck' or 'eagle' sub-types in the 'birds' class) \cite{Icons50}.
 
@@
     \item class - an integer between 0 and 49 representing the icon's class
-    \item subtype - a string corresponding to the class subtype, e.g., ``broken\_heart" for the class ``heart" (label 26)
+    \item sub-type - a string corresponding to the class sub-type, e.g., ``broken\_heart" for the class ``heart" (label 26)
     \item style - a string corresponding to the icon's source, such as Microsoft or Apple
@@
 
-When analyzing the class distribution, we came to the conclusion that the Icons-50 dataset was considerably unbalanced, as seen in Fig.~\ref{fig:Icons50ClassDist}.
+When analyzing the class distribution, I came to the conclusion that the Icons-50 dataset was considerably unbalanced, as seen in Fig.~\ref{fig:Icons50ClassDist}.
 
@@
 \subsection{Methods}
-We opted to adapt an already existing implementation of a cGAN model using the \texttt{keras} library, with the original source code available in \cite{BrownleeCGAN, BrownleeGAN}.
+I opted to adapt an already existing implementation of a cGAN model using the \texttt{keras} library, with the original source code available in \cite{BrownleeCGAN, BrownleeGAN}.
 In the original post, the author chooses to train the model with the MNIST Fashion dataset, which is comprised of gray-level images with 28x28 pixels, far different from the Icons-50 dataset specifications.
 
-In the case of a regular GAN, in Fig.~\ref{fig:GANArch}, the generator takes in the input vector randomly drawn from the latent space and outputs the generated image, which is fed to the discriminator, along side real examples from our dataset, and outputs a classification: whether or not it is real.
+In the case of a regular GAN, in Fig.~\ref{fig:GANArch}, the generator takes in the input vector randomly drawn from the latent space and outputs the generated image, which is fed to the discriminator, along side real examples from the dataset, and outputs a classification: whether or not it is real.
 
@@
 The main difference between the regular GAN and the cGAN models can be seen in Fig.~\ref{fig:cGANArch}.
-The conditioning variable, in our case, is the icon's class label, which is fed both to the generator when generating a new fake icon, and to the discriminator in order to learn whether or not it belongs to the specific class.
+The conditioning variable, in this case, is the icon's class label, which is fed both to the generator when generating a new fake icon, and to the discriminator in order to learn whether or not it belongs to the specific class.
 
@@
 
-With all this in mind, we built our model, starting with the generator.
+With all this in mind, I built the model, starting with the generator.
 
-As it is clear from Fig.~\ref{fig:GenStruct}, the generator takes in the class label of the icon we want to generate and an input vector drawn randomly from the latent space, with a dimension set at 100.
+As it is clear from Fig.~\ref{fig:GenStruct}, the generator takes in the class label of the icon I want to generate and an input vector drawn randomly from the latent space, with a dimension set at 100.
 It has a total of 1.38M parameters.
 
-In terms of the activation layers, we opted for the leaky RELU with an alpha of 0.2, apart from the output layer with a \textit{tanh} activation.
+In terms of the activation layers, I opted for the leaky ReLU with an alpha of 0.2, apart from the output layer with a \textit{tanh} activation.
 
@@
 
-Now for the discriminator, as it is evident from (Fig.~\ref{fig:DiscStruct}), we again chose the leaky RELU function with an alpha of 0.2 for most of the model, apart from the output, which in this case has a \textit{sigmoid} activation, as we are dealing with a binary classification problem.
+Now for the discriminator, as it is evident from (Fig.~\ref{fig:DiscStruct}), I again chose the leaky ReLU function with an alpha of 0.2 for most model layers, apart from the output, which in this case has a \textit{sigmoid} activation, as I are dealing with a binary classification problem.
 
@@
 
-Finally, we assemble our cGAN model by taking the generator's output and the input class label and feeding them to the discriminator, as seen in Fig.~\ref{fig:cGANStruct}.
+Finally, I assemble the cGAN model by taking the generator's output and the input class label and feeding them to the discriminator, as seen in Fig.~\ref{fig:cGANStruct}.
 
@@
 
-We chose to train trained two models with identical architectures, first with our original dataset, the Icons-50, and then with the new Icons-10 subset.
-Given the smaller dataset, we picked an appropriate batch size to match its length, seen in Table~\ref{tab:ModelParams}.
+I chose to train trained two models with identical architectures, first with the original dataset, the Icons-50, and then with the new Icons-10 subset.
+Given the smaller dataset, I picked an appropriate batch size to match its length, seen in Table~\ref{tab:ModelParams}.
 
@@
 
-After training our model with the Icons-50 dataset for 100 epochs, we were able to achieve a remarkable classification accuracy on the discriminator, seen in Fig.~\ref{fig:Icons50Acc}, with a 94\% accuracy for real images and a 98\% accuracy for generated images.
+After training the model with the Icons-50 dataset for 100 epochs, I was able to achieve a remarkable classification accuracy on the discriminator, seen in Fig.~\ref{fig:Icons50Acc}, with a 94\% accuracy for real images and a 98\% accuracy for generated images.
 
@@
 
-Afterwards, we trained a new model, with the same structure, on the Icons-10 subset, again for 100 epochs.
+Afterwards, I trained a new model, with the same structure, on the Icons-10 subset, again for 100 epochs.
 When analyzing the discriminator's performance, it seemed that both its loss and accuracy suffered.
@@
 
-To better evaluate the performance of the trained generators, we generated a new set of icons belonging to the classes common to both datasets.
+To better evaluate the performance of the trained generators, I generated a new set of icons belonging to the classes common to both datasets.
 
@@
 
- Possibly due to the large number of classes, the model seemed to overfit the data (Icons-50) and the generator loss kept increasing as the training continued, finishing with a not so great loss.
+When dealing with imbalanced data, such as the Icons-50 dataset, it is important to consider how this may impact the training of a machine learning (ML) model, especially when the number of classes is large.
+
+When trained with the original unfiltered data, the discriminator was able to achieve a high accuracy of around 96\% and a small loss of 0.329.
+While these results would be optimal in their own, when analyzed alongside the generator's performance, the model seemed to overfit the data, possibly due to the large number of classes, finishing off with a disappointing loss of 2.532.
+
+Afterwards, I decided to filter out the dataset by choosing the 10 most frequent classes, in the hope that when training a new model, I would be able to achieve better results when it came to the icon generation.
+I called this new dataset, fittingly, the Icons-10 dataset.
+
+I then trained a new model with an identical structure to the first one, but now on the filtered data.
+As to be expected, while the discriminator suffered a slight dip in performance, with an accuracy of 85\% and a loss of 1.433, the generator improved quite significantly, with a lower loss of 1.433.
+
+When analyzing the icons generated by each model, it became apparent that, while the first model was able to learn the overall structure and element composition of the icon, particularly in the case of the ``family" class, the results were lackluster and lacked the proper detail to discern what they represented, without the added context, as seen in Fig.~\ref{fig:Icons50Clock},\ref{fig:Icons50Family}.
+
+This suggests that the generator may not have been deep or large enough to learn the necessary features for generating icons for 50 different classes, while the model trained with the Icons-10 dataset was able to learn and generated detailed and striking images, such as Fig.~\ref{fig:Icons10Clock},\ref{fig:Icons10Family}.
 
 \section{Conclusions}
-Overall, cGANs are an important tool in the field of machine learning, as they allow the generation of data with specific characteristics, which can be useful in a wide range of applications.
+In this paper, the ability of conditional generative adversarial networks (cGANs) to generate icons with specific characteristics or properties was explored using the Icons-50 dataset.
+To address the issue of imbalanced data in the original unfiltered dataset, a new dataset was created by filtering the original dataset to include only the 10 most frequent classes (the Icons-10 dataset).
+
+When comparing the performance of the cGANs trained on these two datasets, it was found that the model trained on the Icons-10 dataset was able to generate more detailed and striking icons compared to the model trained on the unfiltered data.
+This suggests that the model trained on the Icons-10 dataset was able to learn more effectively and generate more accurate and representative icons for the desired classes.
+
+In conclusion, cGANs can be an effective tool for generating icons with specific characteristics or properties, given a suitable dataset.
+In this case, filtering the original dataset to include only the most frequent classes improved the performance of the cGANs, demonstrating the importance of considering the impact of imbalanced data on model training.
+
+Future work could include testing the performance of cGANs with different hyper-parameters or architectures, or using a different dataset with more balanced class distribution.
+Additionally, exploring the use of cGANs for generating icons with other specific characteristics or properties, such as color or shape, could be a valuable direction for future research
 

### 2023-01-07 paper/article.tex
updated article

@@
 
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+\newcommand{\BibTeX}{{\textrm{B} \kern-.05em{\textsc{i} \kern-.025em b}\kern-.08em
 T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
@@
 
-\section{Introduction}
-\subsection{Background}
-Conditional Generative Adversarial Networks (cGANs) \cite{Mirza2014} are a variant of Generative Adversarial Networks (GANs) that allow the generation of new data samples with specific properties or characteristics.
-They consist of two neural networks: a generator and a discriminator.
-The generator is trained to generate new data samples that are similar to a training set, while the discriminator is trained to distinguish between real and fake data samples.
+    \section{Introduction}\label{sec:introduction}
+    \input{sections/introduction}
 
-cGANs introduce an additional input to the generator and discriminator networks, known as the conditioning variable, which allows the model to generate data with specific characteristics or properties.
-This can be useful in a variety of applications, such as image generation, text generation, and speech generation, where the output data needs to have specific attributes or features \cite{Mirza2014}.
+    \section{Materials and Methods}\label{sec:materials-and-methods}
+    \input{sections/materials-and-methods}
 
-For example, in image generation, the conditioning variable may be a label indicating the class of the image to be generated (e.g., a specific type of animal or object), or it may be an attribute of the image (e.g., the presence or absence of a certain color).
+    \section{Results}\label{sec:results}
+    \input{sections/results}
 
-\subsection{Problem}
-Given a public dataset, Icons-50 \cite{Icons50, Hendrycks2018}, comprised of icons and their respective labels, I want to be able to generate a new set of sample icons corresponding to a specific label, such as ``clock" or ``airplane".
-
-This could be useful in applications where a large number of icons with specific characteristics are needed, such as in user interface design or graphics design.
-
-\subsection{Objective}
-Using cGANs, it is possible to generate icons with specific characteristics or properties, given a public dataset such as Icons-50.
-To do this, the cGAN would be trained on said dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat" or ``bird".
-
-\subsection{Related Work}
-In Mirza and Osindero \cite{Mirza2014}, the authors introduce the concept of conditional generative adversarial networks (cGANs), which are a variant of generative adversarial networks (GANs) that allow the generation of new data samples with specific properties or characteristics.
-The cGANs are constructed by feeding the data and the desired characteristics or properties to both the generator and discriminator networks.
-The authors demonstrate the use of cGANs for generating MNIST digits conditioned on class labels and for learning a multi-modal model.
-They also provide examples of using cGANs for image tagging, where the model is able to generate descriptive tags that are not part of the training labels.
-
-In Liu et al.
-\cite{Liu2021SCCGAN:CGAN}, the authors propose a cGAN-based method for repairing damaged fonts based on style.
-They use the content accuracy and style similarity of the repaired font as evaluation indices to assess the accuracy of the restored style.
-The results show that the cGAN-based method is able to repair damaged fonts in a way that is similar to the correct content.
-
-In Loey et al.
-\cite{Loey2020AImages}, the authors propose the use of classical data augmentation techniques along with a cGAN based on a deep transfer learning model for COVID-19 detection in chest CT scan images.
-The motivation for this research was the limited availability of benchmark datasets for COVID-19, particularly in chest CT images.
-To address this, the authors collected all available images for COVID-19 and used classical data augmentation techniques along with a cGAN to generate additional images to help in the detection of the virus.
-The results showed that the classical data augmentation techniques along with the cGAN improved the performance of classification in all selected models.
-
-In Ma et al.
-\cite{Ma2018SpeckleCGAN}, the authors propose an end-to-end framework based on a cGAN for simultaneously reducing speckle noise and enhancing contrast in retinal OCT images.
-The cGAN is trained using a novel method for obtaining clean images from outputs of commercial OCT scanners, and an edge loss function is added to the final objective to ensure that the model is sensitive to edge-related details.
-The results show that the proposed method outperforms traditional and other deep learning methods in terms of denoising performance, and has good generalization ability for different types of retinal OCT images.
-
-\section{Materials and Methods}
-
-\subsection{Data}
-To achieve my goal, I opted for the public dataset ``Icons-50" \cite{Icons50}, first introduced in \cite{Hendrycks2018}.
-According to the authors, this dataset was initially designed to test the robustness of classifiers to surface variations in objects.
-The dataset includes both new styles of known objects and unexpected instances of known classes, and the authors propose two methods to improve the surface variation robustness of classifiers.
-
-The Icons-50 dataset consists of 10,000 images belonging to 50 classes of icons (e.g., people, food, activities, places, objects, symbols, etc.) collected from different technology companies and platforms (e.g., Apple, Samsung, Google, Facebook, etc.).
-
-Each class has icons with different styles (e.g., Microsoft's flat vector graphics icon style) and different class sub-types (e.g., 'duck' or 'eagle' sub-types in the 'birds' class) \cite{Icons50}.
-
-To summarize, each entry in the dataset is comprised of the following parameters:
-\begin{itemize}
-    \item image - a 3x32x32 NumPy array corresponding to the RGB icon
-    \item class - an integer between 0 and 49 representing the icon's class
-    \item sub-type - a string corresponding to the class sub-type, e.g., ``broken\_heart" for the class ``heart" (label 26)
-    \item style - a string corresponding to the icon's source, such as Microsoft or Apple
-    \item rendition - an integer between 0 and 9 representing the icon's version
-\end{itemize}
-
-When analyzing the class distribution, I came to the conclusion that the Icons-50 dataset was considerably unbalanced, as seen in Fig.~\ref{fig:Icons50ClassDist}.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/icons50/class_dist.png}
-    \caption{Class distribution of the Icons-50 dataset}
-    \label{fig:Icons50ClassDist}
-\end{figure}
-
-This led to the creation of Icons-10, a subset of Icons-50 containing the top 10 most frequent classes in the dataset, with the old labels mapped to new values between 0 and 9.
-The Icons-10 dataset comprises 4170 images and has a fairly balanced class distribution, seen both in Fig.~\ref{fig:Icons10ClassDist} and in Table~\ref{tab:Icons10Desc}.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/icons10/class_dist.png}
-    \caption{Class distribution of the Icons-10 dataset}
-    \label{fig:Icons10ClassDist}
-\end{figure}
-
-\begin{table}[htbp]
-    \centering
-    \caption{Icons-10 Dataset}
-    \begin{tabular}{cccc}
-    \hline
-    \textbf{Class} & \textbf{Old label} & \textbf{New label} & \textbf{No. samples} \\ \hline
-    worker & 47 & 0 & 487  \\ 
-    family & 17 & 1 & 455  \\
-    flag & 20 & 2 & 446  \\
-    face & 15 & 3 & 429  \\
-    hands & 24 & 4 & 429  \\
-    clock & 11 & 5 & 417  \\
-    heart & 26 & 6 & 396  \\
-    arrow & 1 & 7 & 392  \\
-    cat & 19 & 8 & 363  \\
-    ideograph & 28 & 9 & 356 \\ \hline
-    \end{tabular}
-    \label{tab:Icons10Desc}
-\end{table}
-
-\subsection{Methods}
-I opted to adapt an already existing implementation of a cGAN model using the \texttt{keras} library, with the original source code available in \cite{BrownleeCGAN, BrownleeGAN}.
-In the original post, the author chooses to train the model with the MNIST Fashion dataset, which is comprised of gray-level images with 28x28 pixels, far different from the Icons-50 dataset specifications.
-
-In the case of a regular GAN, in Fig.~\ref{fig:GANArch}, the generator takes in the input vector randomly drawn from the latent space and outputs the generated image, which is fed to the discriminator, along side real examples from the dataset, and outputs a classification: whether or not it is real.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/architecture/gan_arch.png}
-    \caption{Architecture of traditional Generative Adversarial Networks (GANs)}
-    \label{fig:GANArch}
-\end{figure}
-
-The main difference between the regular GAN and the cGAN models can be seen in Fig.~\ref{fig:cGANArch}.
-The conditioning variable, in this case, is the icon's class label, which is fed both to the generator when generating a new fake icon, and to the discriminator in order to learn whether or not it belongs to the specific class.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/architecture/cgan_arch.png}
-    \caption{Architecture of Conditional Generative Adversarial Networks (cGANs)}
-    \label{fig:cGANArch}
-\end{figure}
-
-With all this in mind, I built the model, starting with the generator.
-
-As it is clear from Fig.~\ref{fig:GenStruct}, the generator takes in the class label of the icon I want to generate and an input vector drawn randomly from the latent space, with a dimension set at 100.
-It has a total of 1.38M parameters.
-
-In terms of the activation layers, I opted for the leaky ReLU with an alpha of 0.2, apart from the output layer with a \textit{tanh} activation.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.4\textwidth]{paper/images/summary/generator.png}
-    \caption{Structure of the generator model}
-    \label{fig:GenStruct}
-\end{figure}
-
-Now for the discriminator, as it is evident from (Fig.~\ref{fig:DiscStruct}), I again chose the leaky ReLU function with an alpha of 0.2 for most model layers, apart from the output, which in this case has a \textit{sigmoid} activation, as I are dealing with a binary classification problem.
-
-Since the discriminator is to be trained individually, it must be compiled with a given optimizer, in this case, the Adam optimizer, with a learning rate $LR=\num{2e-4}$ and a $\beta_1=0.5$.
-It has a total of 0.22M parameters.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.4\textwidth]{paper/images/summary/discriminator.png}
-    \caption{Structure of the discriminator model}
-    \label{fig:DiscStruct}
-\end{figure}
-
-Finally, I assemble the cGAN model by taking the generator's output and the input class label and feeding them to the discriminator, as seen in Fig.~\ref{fig:cGANStruct}.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/summary/cgan.png}
-    \caption{Structure of the cGAN model}
-    \label{fig:cGANStruct}
-\end{figure}
-
-I chose to train trained two models with identical architectures, first with the original dataset, the Icons-50, and then with the new Icons-10 subset.
-Given the smaller dataset, I picked an appropriate batch size to match its length, seen in Table~\ref{tab:ModelParams}.
-
-\begin{table}[htbp]
-    \centering
-    \caption{Model parameters}
-    \begin{tabular}{ccccc}
-    \hline
-    \textbf{Dataset} & \textbf{Parameters} & \textbf{Epochs} & \textbf{Batch Size} & \textbf{Latent Dim} \\ \hline
-    Icons-50 & 1.6M & 100 & 50 & 100 \\
-    Icons-10 & 1.6M & 100 & 30 & 100 \\ \hline
-    \end{tabular}
-    \label{tab:ModelParams}
-\end{table}
-
-\section{Results}
-
-After training the model with the Icons-50 dataset for 100 epochs, I was able to achieve a remarkable classification accuracy on the discriminator, seen in Fig.~\ref{fig:Icons50Acc}, with a 94\% accuracy for real images and a 98\% accuracy for generated images.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/icons50/icons50_acc.png}
-    \caption{Discriminator accuracy on the Icons-50 dataset}
-    \label{fig:Icons50Acc}
-\end{figure}
-
-In terms of loss, while the discriminator finished with a satisfactory minimal loss of 0.329, the same could not be said for the generator, as its loss kept increasing as the training went along, finishing at a value of around 2.532, as can be seen in Fig.~\ref{fig:Icons50Loss}.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/icons50/icons50_loss.png}
-    \caption{Model loss on the Icons-50 dataset}
-    \label{fig:Icons50Loss}
-\end{figure}
-
-Afterwards, I trained a new model, with the same structure, on the Icons-10 subset, again for 100 epochs.
-When analyzing the discriminator's performance, it seemed that both its loss and accuracy suffered.
-
-While the loss only increased slightly, to an acceptable value of 0.643, the accuracy while classifying images as real or fake varied quite drastically during training, as can be seen on Fig.~\ref{fig:Icons10Acc}, finishing at, respectively, 83.33\% and 86.67\%.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/icons10/icons10_acc.png}
-    \caption{Discriminator accuracy on the Icons-10 dataset}
-    \label{fig:Icons10Acc}
-\end{figure}
-
-In terms of the generator's performance, while the loss still varied quite significantly, the the new dataset proved successful, with the model finishing with a much better loss of 1.433, as seen on Fig.~\ref{fig:Icons10Loss}.
-
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.48\textwidth]{paper/images/icons10/icons10_loss.png}
-    \caption{Model loss on the Icons-10 dataset}
-    \label{fig:Icons10Loss}
-\end{figure}
-
-To better evaluate the performance of the trained generators, I generated a new set of icons belonging to the classes common to both datasets.
-
-\begin{figure}[htbp]
-    \begin{subfigure}[h]{0.4\linewidth}
-        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons50_clock.png}
-        \caption{Icons-50 dataset}
-        \label{fig:Icons50Clock}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[h]{0.4\linewidth}
-        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons10_clock.png}
-        \caption{Icons-10 dataset}
-        \label{fig:Icons10Clock}
-    \end{subfigure}
-    \caption{Generated icons belonging to class ``clock"}
-    \label{fig:ClockIcons}
-\end{figure}
-
-When given a simple task, such as generating a ``clock" icon, the model trained on the Icons-50 dataset only seemed to perceive the shape of the clock, with none of the defining details being present in the generated images, evident from Fig.~\ref{fig:Icons50Clock}.
-
-The second model performed much better on this task, capturing finer details such as the correct color, and the hour and minutes hands, as it is clear from Fig.~\ref{fig:Icons10Clock}.
-
-\begin{figure}[htbp]
-    \begin{subfigure}[h]{0.4\linewidth}
-        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons50_family.png}
-        \caption{Icons-50 dataset}
-        \label{fig:Icons50Family}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[h]{0.4\linewidth}
-        \includegraphics[width=\linewidth]{paper/images/gen_icons/icons10_family.png}
-        \caption{Icons-10 dataset}
-        \label{fig:Icons10Family}
-    \end{subfigure}
-    \caption{Generated icons belonging to class ``family"}
-    \label{fig:FamilyIcons}
-\end{figure}
-
-When dealing with a complex task, such as generating icons for the ``family" class, the original generator was able to create recognizable images, even though they lacked definition and variability, as seen on Fig.~\ref{fig:Icons50Family}.
-
-When trained on the Icons-10 dataset, the model was able to generate a unique and slightly more detailed set of icons, albeit with variable results, as seen on Fig.~\ref{fig:Icons10Family}.
-
-\section{Discussion}
+    \section{Discussion}\label{sec:discussion}
 
@@
 
-When analyzing the icons generated by each model, it became apparent that, while the first model was able to learn the overall structure and element composition of the icon, particularly in the case of the ``family" class, the results were lackluster and lacked the proper detail to discern what they represented, without the added context, as seen in Fig.~\ref{fig:Icons50Clock},\ref{fig:Icons50Family}.
+    When analyzing the icons generated by each model, it became apparent that, while the first model was able to learn the overall structure and element composition of the icon, particularly in the case of the ``family'' class, the results were lackluster and lacked the proper detail to discern what they represented, without the added context, as seen in Fig.~\ref{fig:Icons50Clock},\ref{fig:Icons50Family}.
 
@@
 
-\section{Conclusions}
+    \section{Conclusions}\label{sec:conclusions}
     In this paper, the ability of conditional generative adversarial networks (cGANs) to generate icons with specific characteristics or properties was explored using the Icons-50 dataset.
@@
     \bibliographystyle{IEEEtran}
-\bibliography{paper/references}
+    \bibliography{references}
 

### 2023-01-07 paper/sections/introduction.tex
updated article

\subsection{Background}\label{subsec:background}
Conditional Generative Adversarial Networks (cGANs)~\cite{Mirza2014} are a variant of Generative Adversarial Networks
(GANs) that allow the generation of new data samples with specific properties or characteristics.
They consist of two neural networks: a generator and a discriminator.
The generator is trained to generate new data samples that are similar to a training set, while the discriminator is
trained to distinguish between real and fake data samples.

cGANs introduce an additional input to the generator and discriminator networks, known as the conditioning variable,
which allows the model to generate data with specific characteristics or properties.
This can be useful in a variety of applications, such as image generation, text generation, and speech generation, where
the output data needs to have specific attributes or features~\cite{Mirza2014}.

For example, in image generation, the conditioning variable may be a label indicating the class of the image to be generated (e.g., a specific type of animal or object), or it may be an attribute of the image (e.g., the presence or absence of a certain color).

\subsection{Problem}\label{subsec:problem}
Given a public dataset, Icons-50~\cite{Icons50, Hendrycks2018}, comprised of icons and their respective labels, we want to be able to generate a new set of sample icons corresponding to a specific label, such as ``clock'' or ``airplane''.

This could be useful in applications where a large number of icons with specific characteristics are needed, such as in user interface design or graphics design.

\subsection{Objective}\label{subsec:objective}
Using cGANs, it is possible to generate icons with specific characteristics or properties, given a public dataset such as Icons-50.
To do this, the cGAN would be trained on said dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat'' or ``bird''.

\subsection{Related Work}\label{subsec:related-work}
In Mirza and Osindero~\cite{Mirza2014} , the authors introduce the concept of conditional generative adversarial networks (cGANs), which are a variant of generative adversarial networks (GANs) that allow the generation of new data samples with specific properties or characteristics.
The cGANs are constructed by feeding the data and the desired characteristics or properties to both the generator and discriminator networks.
The authors demonstrate the use of cGANs for generating MNIST digits conditioned on class labels and for learning a multi-modal model.
They also provide examples of using cGANs for image tagging, where the model is able to generate descriptive tags that are not part of the training labels.

In Liu et al.~\cite{Liu2021SCCGAN:CGAN} , the authors propose a cGAN-based method for repairing damaged fonts based on style.
They use the content accuracy and style similarity of the repaired font as evaluation indices to assess the accuracy of the restored style.
The results show that the cGAN-based method is able to repair damaged fonts in a way that is similar to the correct content.

In Loey et al.~\cite{Loey2020AImages} , the authors propose the use of classical data augmentation techniques along with a cGAN based on a deep transfer learning model for COVID-19 detection in chest CT scan images.
The motivation for this research was the limited availability of benchmark datasets for COVID-19, particularly in chest CT images.
To address this, the authors collected all available images for COVID-19 and used classical data augmentation techniques along with a cGAN to generate additional images to help in the detection of the virus.
The results showed that the classical data augmentation techniques along with the cGAN improved the performance of classification in all selected models.

In Ma et al.~\cite{Ma2018SpeckleCGAN} , the authors propose an end-to-end framework based on a cGAN for simultaneously reducing speckle noise and enhancing contrast in retinal OCT images.
The cGAN is trained using a novel method for obtaining clean images from outputs of commercial OCT scanners, and an edge loss function is added to the final objective to ensure that the model is sensitive to edge-related details.
The results show that the proposed method outperforms traditional and other deep learning methods in terms of denoising performance, and has good generalization ability for different types of retinal OCT images.

### 2023-01-07 paper/sections/materials-and-methods.tex
updated article

\subsection{Data}\label{subsec:data}
To achieve our goal, we opted for the public dataset ``Icons-50''~\cite{Icons50} , first introduced in~\cite{Hendrycks2018}.
According to the authors, this dataset was initially designed to test the robustness of classifiers to surface variations in objects.
The dataset includes both new styles of known objects and unexpected instances of known classes, and the authors propose two methods to improve the surface variation robustness of classifiers.

The Icons-50 dataset consists of 10,000 images belonging to 50 classes of icons (e.g., people, food, activities, places, objects, symbols, etc.) collected from different technology companies and platforms (e.g., Apple, Samsung, Google, Facebook, etc.).
Each class has icons with different styles (e.g., Microsoft's flat vector graphics icon style) and different class subtypes (e.g., `duck' or `eagle' subtypes in the `birds' class)~\cite{Icons50}.

To summarize, each entry in the dataset consists of the following parameters:
\begin{itemize}
    \item image - a 3x32x32 NumPy array corresponding to the RGB icon
    \item class - an integer between 0 and 49 representing the icon's class
    \item subtype - a string corresponding to the class subtype, e.g., ``broken\_heart'' for the class ``heart'' (label 26)
    \item style - a string corresponding to the icon's source, such as Microsoft or Apple
    \item rendition - an integer between 0 and 9 representing the icon's version
\end{itemize}

When analyzing the class distribution, we came to the conclusion that the Icons-50 dataset was considerably unbalanced, as seen in Fig.~\ref{fig:Icons50ClassDist}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/icons50/class_dist}
    \caption{Class distribution of the Icons-50 dataset}
    \label{fig:Icons50ClassDist}
\end{figure}

This led to the creation of Icons-10, a subset of Icons-50 containing the top 10 most frequent classes in the dataset, with the old labels mapped to new values between 0 and 9.
The Icons-10 dataset comprises 4170 images and has a fairly balanced class distribution, seen both in Fig.~\ref{fig:Icons10ClassDist} , and in Table~\ref{tab:Icons10Desc}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/icons10/class_dist}
    \caption{Class distribution of the Icons-10 dataset}
    \label{fig:Icons10ClassDist}
\end{figure}

\begin{table}[htbp]
    \centering
    \caption{Icons-10 Dataset}
    \begin{tabular}{cccc}
        \hline
        \textbf{Class} & \textbf{Old label} & \textbf{New label} & \textbf{No. samples} \\ \hline
        worker         & 47                 & 0                  & 487                  \\
        family         & 17                 & 1                  & 455                  \\
        flag           & 20                 & 2                  & 446                  \\
        face           & 15                 & 3                  & 429                  \\
        hands          & 24                 & 4                  & 429                  \\
        clock          & 11                 & 5                  & 417                  \\
        heart          & 26                 & 6                  & 396                  \\
        arrow          & 1                  & 7                  & 392                  \\
        cat            & 19                 & 8                  & 363                  \\
        ideograph      & 28                 & 9                  & 356                  \\ \hline
    \end{tabular}
    \label{tab:Icons10Desc}
\end{table}

\subsection{Methods}\label{subsec:methods}
We opted to adapt an already existing implementation of a cGAN model using the \texttt{keras} library, with the original source code available in~\cite{BrownleeCGAN, BrownleeGAN}.
In the original post, the author chooses to train the model with the MNIST Fashion dataset, which comprises gray-level images with 28x28 pixels, far different from the Icons-50 dataset specifications.

In the case of a regular GAN, in Fig.~\ref{fig:GANArch}, the generator takes in the input vector randomly drawn from the latent space and outputs the generated image, which is fed to the discriminator, alongside real examples from our dataset, and outputs a classification: whether it is real.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/architecture/gan_arch}
    \caption{Architecture of traditional Generative Adversarial Networks (GANs)}
    \label{fig:GANArch}
\end{figure}

The main difference between the regular GAN and the cGAN models can be seen in Fig.~\ref{fig:cGANArch}.
The conditioning variable, in our case, is the icon's class label, which is fed both to the generator when generating a new fake icon, and to the discriminator in order to learn whether it belongs to the specific class.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/architecture/cgan_arch}
    \caption{Architecture of Conditional Generative Adversarial Networks (cGANs)}
    \label{fig:cGANArch}
\end{figure}

With all this in mind, we built our model, starting with the generator.

As it is clear from Fig.~\ref{fig:GenStruct} , the generator takes in the class label of the icon we want to generate and an input vector drawn randomly from the latent space, with a dimension set at 100.
It has a total of 1.38M parameters.

In terms of the activation layers, we opted for the leaky RELU with an alpha of 0.2, apart from the output layer with a \textit{tanh} activation.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.4\textwidth]{images/summary/generator}
    \caption{Structure of the generator model}
    \label{fig:GenStruct}
\end{figure}

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.4\textwidth]{images/summary/discriminator}
    \caption{Structure of the discriminator model}
    \label{fig:DiscStruct}
\end{figure}

Now for the discriminator, as it is evident from (Fig.~\ref{fig:DiscStruct}), we again chose the leaky RELU function with an alpha of 0.2 for most of the model, apart from the output, which in this case has a \textit{sigmoid} activation, as we are dealing with a binary classification problem.

Since the discriminator is to be trained individually, it must be compiled with a given optimizer, in this case, the Adam optimizer, with a learning rate $LR=\num{2e-4}$ and a $\beta_1=0.5$.
It has a total of 0.22M parameters.

Finally, we assemble our cGAN model by taking the generator's output and the input class label and feeding them to the discriminator, as seen in Fig.~\ref{fig:cGANStruct}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/summary/cgan}
    \caption{Structure of the cGAN model}
    \label{fig:cGANStruct}
\end{figure}

We chose to train trained two models with identical architectures, first with our original dataset, the Icons-50, and then with the new Icons-10 subset.
Given the smaller dataset, we picked an appropriate batch size to match its length, seen in Table~\ref{tab:ModelParams}.

\begin{table}[htbp]
    \centering
    \caption{Model parameters}
    \begin{tabular}{ccccc}
        \hline
        \textbf{Dataset} & \textbf{Parameters} & \textbf{Epochs} & \textbf{Batch Size} & \textbf{Latent Dim} \\ \hline
        Icons-50         & 1.6M                & 100             & 50                  & 100                 \\
        Icons-10         & 1.6M                & 100             & 30                  & 100                 \\ \hline
    \end{tabular}
    \label{tab:ModelParams}
\end{table}

### 2023-01-07 paper/sections/results.tex
updated article

After training the model with the Icons-50 dataset for 100 epochs, I was able to achieve a remarkable classification accuracy on the discriminator, seen in Fig.~\ref{fig:Icons50Acc} , with a 94\% accuracy for real images and a 98\% accuracy for generated images.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/icons50/icons50_acc}
    \caption{Discriminator accuracy on the Icons-50 dataset}
    \label{fig:Icons50Acc}
\end{figure}

In terms of loss, while the discriminator finished with a satisfactory minimal loss of 0.329, the same could not be said for the generator, as its loss kept increasing as the training went along, finishing at a value of around 2.532, as can be seen in Fig.~\ref{fig:Icons50Loss} .

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/icons50/icons50_loss}
    \caption{Model loss on the Icons-50 dataset}
    \label{fig:Icons50Loss}
\end{figure}

Afterwards, I trained a new model, with the same structure, on the Icons-10 subset, again for 100 epochs.
When analyzing the discriminator's performance, it seemed that both its loss and accuracy suffered.

While the loss only increased slightly, to an acceptable value of 0.643, the accuracy while classifying images as real or fake varied quite drastically during training, as can be seen on Fig.~\ref{fig:Icons10Acc} , finishing at, respectively, 83.33\% and 86.67\%.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/icons10/icons10_acc}
    \caption{Discriminator accuracy on the Icons-10 dataset}
    \label{fig:Icons10Acc}
\end{figure}

In terms of the generator's performance, while the loss still varied quite significantly, the new dataset proved successful, with the model finishing with a much better loss of 1.433, as seen on Fig.~\ref{fig:Icons10Loss} .

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.48\textwidth]{images/icons10/icons10_loss}
    \caption{Model loss on the Icons-10 dataset}
    \label{fig:Icons10Loss}
\end{figure}

To better evaluate the performance of the trained generators, I generated a new set of icons belonging to the classes common to both datasets.

\begin{figure}[htbp]
    \begin{subfigure}[h]{0.4\linewidth}
        \includegraphics[width=\linewidth]{images/gen_icons/icons50_clock}
        \caption{Icons-50 dataset}
        \label{fig:Icons50Clock}
    \end{subfigure}
    \hfill
    \begin{subfigure}[h]{0.4\linewidth}
        \includegraphics[width=\linewidth]{images/gen_icons/icons10_clock}
        \caption{Icons-10 dataset}
        \label{fig:Icons10Clock}
    \end{subfigure}
    \caption{Generated icons belonging to class ``clock"}
\end{figure}

When given a simple task, such as generating a ``clock'' icon, the model trained on the Icons-50 dataset only seemed to perceive the shape of the clock, with none of the defining details being present in the generated images, evident from Fig.~\ref{fig:Icons50Clock}.

The second model performed much better on this task, capturing finer details such as the correct color, and the hour and minutes hands, as it is clear from Fig.~\ref{fig:Icons10Clock} .

\begin{figure}[htbp]
    \begin{subfigure}[h]{0.4\linewidth}
        \includegraphics[width=\linewidth]{images/gen_icons/icons50_family}
        \caption{Icons-50 dataset}
        \label{fig:Icons50Family}
    \end{subfigure}
    \hfill
    \begin{subfigure}[h]{0.4\linewidth}
        \includegraphics[width=\linewidth]{images/gen_icons/icons10_family}
        \caption{Icons-10 dataset}
        \label{fig:Icons10Family}
    \end{subfigure}
    \caption{Generated icons belonging to class ``family"}
\end{figure}

When dealing with a complex task, such as generating icons for the ``family'' class, the original generator was able to create recognizable images, even though they lacked definition and variability, as seen on Fig.~\ref{fig:Icons50Family}.

When trained on the Icons-10 dataset, the model was able to generate a unique and slightly more detailed set of icons, albeit with variable results, as seen on Fig.~\ref{fig:Icons10Family}.

### 2023-01-07 model/train.py

@@ -59,9 +59,9 @@ def train_cgan(cgan: Functional, generator: Functional, discriminator: Functiona
             # update the generator via the discriminator's error
             g_loss = cgan.train_on_batch([z_input, labels_input], y_gan)
             # calculate the discriminator loss
-            d_loss = 0.5 * np.add(d_loss1, d_loss2)
+            d_loss = (d_loss1 + d_loss2) / 2.0
             # calculate the discriminator accuracy
-            d_acc = 0.5 * np.add(d_acc1, d_acc2)
+            d_acc = (d_acc1 + d_acc2) / 2.0
             # summarize loss on this batch
             print(f'\r> Epoch {epoch + 1}: '
                   f'Batch {batch + 1}/{batches_per_epoch}, '

### 2023-01-08 config/config.py
new and improved README.md

@@ -11,6 +11,7 @@ class Optimizer:
 class Params:
     latent_dim: int
     num_classes: int
+    top_k: int
     image_size: int
     channels: int
     epochs: int

### 2023-01-08 test.py

@@ -1,0 +1,47 @@
+import os
+
+import hydra
+from hydra.core.config_store import ConfigStore
+
+from config.config import Icons50Config
+from ds.dataset import Icons50Dataset, read_classes, read_label
+from ds.generation import generate_images
+from model.train import load_generator
+
+cs = ConfigStore.instance()
+cs.store(name="icons50_config", node=Icons50Config)
+
+
+@hydra.main(version_base=None, config_path="config", config_name="config")
+def main(cfg: Icons50Config) -> None:
+    """ Main function """
+    # suppress TensorFlow INFO messages
+    os.environ['TF_CPP_MIN_LOG_LEVEL'] = '1'
+    # Read classes
+    classes = read_classes(cfg.paths.classes_path)
+    # Load dataset
+    dataset = Icons50Dataset.from_pickle(
+        path=cfg.paths.data_path,
+        classes=classes,
+    )
+    # Show dataset summary
+    dataset.summary()
+    # Filter the dataset
+    if cfg.params.top_k > 0:
+        dataset = dataset.filter(cfg.params.top_k)
+        cfg.params.num_classes = cfg.params.top_k
+    # load saved generator model
+    generator = load_generator(path=cfg.paths.filt_save_path)
+    # Read the label from user input
+    label = read_label(num_classes=cfg.params.num_classes)
+    dataset.print_subtypes(label)
+    # generate images
+    generate_images(
+        generator=generator,
+        label=label,
+        latent_dim=cfg.params.latent_dim
+    )
+
+
+if __name__ == "__main__":
+    main()

### 2023-01-08 train.py

@@ -4,10 +4,9 @@ import hydra
 from hydra.core.config_store import ConfigStore
 
 from config.config import Icons50Config
-from ds.dataset import Icons50Dataset, read_classes, read_label
-from ds.generation import generate_images
+from ds.dataset import Icons50Dataset, read_classes
 from model.cgan import create_discriminator, create_generator, create_cgan
-from model.train import save_models, train_cgan, load_generator
+from model.train import save_models, train_cgan
 
 cs = ConfigStore.instance()
 cs.store(name="icons50_config", node=Icons50Config)
@@ -25,10 +24,14 @@ def main(cfg: Icons50Config) -> None:
         path=cfg.paths.data_path,
         classes=classes,
     )
-    # Preprocess the dataset
-    dataset.preprocess()
     # Show dataset summary
     dataset.summary()
+    # Preprocess the dataset
+    dataset.preprocess()
+    # Filter the dataset
+    if cfg.params.top_k > 0:
+        dataset = dataset.filter(cfg.params.top_k)
+        cfg.params.num_classes = cfg.params.top_k
     # Shuffle the dataset
     if cfg.params.shuffle:
         dataset.shuffle()
@@ -73,20 +76,7 @@ def main(cfg: Icons50Config) -> None:
         generator=generator,
         discriminator=discriminator,
         cgan=cgan,
-        path=cfg.paths.save_path
-    )
-    # filter the dataset
-    filtered_ds = dataset.filter(top_k=10)
-    # load saved generator model
-    generator = load_generator(path=cfg.paths.filt_save_path)
-    # Read the label from user input
-    label = read_label(num_classes=cfg.params.num_classes)
-    filtered_ds.print_subtypes(label)
-    # generate images
-    generate_images(
-        generator=generator,
-        label=label,
-        latent_dim=cfg.params.latent_dim
+        path=cfg.paths.save_path if cfg.params.top_k == 0 else cfg.paths.filt_save_path,
     )
 
 

### 2023-01-08 paper/article.tex
footnote -> reference to github repo
missing full stop

@@
     Future work could include testing the performance of cGANs with different hyper-parameters or architectures, or using a different dataset with more balanced class distribution.
-    Additionally, exploring the use of cGANs for generating icons with other specific characteristics or properties, such as color or shape, could be a valuable direction for future research
+    Additionally, exploring the use of cGANs for generating icons with other specific characteristics or properties, such as color or shape, could be a valuable direction for future research.
 

### 2023-01-08 paper/src/sections/introduction.tex
LaTeX IntelliJ project

--- 2023-01-07 paper/sections/introduction.tex
@@
 Using cGANs, it is possible to generate icons with specific characteristics or properties, given a public dataset such as Icons-50.
-To do this, the cGAN would be trained on said dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat'' or ``bird''.
+To do so, the cGAN would be trained on said dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat'' or ``bird''.
+\footnote{Source code and trained models are available at   \url{https://github.com/Necas209/Icon-Generation-cGANs}}
 

### 2023-01-08 paper/src/sections/results.tex
LaTeX IntelliJ project

--- 2023-01-07 paper/sections/results.tex
@@
 
+When given a simple task, such as generating a ``clock'' icon, the model trained on the Icons-50 dataset only seemed to perceive the shape of the clock, with none of the defining details being present in the generated images, evident from Fig.~\ref{fig:Icons50Clock}.
+
+The second model performed much better on this task, capturing finer details such as the correct color, and the hour and minutes hands, as it is clear from Fig.~\ref{fig:Icons10Clock}.
+
 \begin{figure}[htbp]
@@
 
-When given a simple task, such as generating a ``clock'' icon, the model trained on the Icons-50 dataset only seemed to perceive the shape of the clock, with none of the defining details being present in the generated images, evident from Fig.~\ref{fig:Icons50Clock}.
+When dealing with a complex task, such as generating icons for the ``family'' class, the original generator was able to create recognizable images, even though they lacked definition and variability, as seen on Fig.~\ref{fig:Icons50Family}.
 
-The second model performed much better on this task, capturing finer details such as the correct color, and the hour and minutes hands, as it is clear from Fig.~\ref{fig:Icons10Clock} .
+When trained on the Icons-10 dataset, the model was able to generate a unique and slightly more detailed set of icons, albeit with variable results, as seen on Fig.~\ref{fig:Icons10Family}.
 
@@
 \end{figure}
-
-When dealing with a complex task, such as generating icons for the ``family'' class, the original generator was able to create recognizable images, even though they lacked definition and variability, as seen on Fig.~\ref{fig:Icons50Family}.
-
-When trained on the Icons-10 dataset, the model was able to generate a unique and slightly more detailed set of icons, albeit with variable results, as seen on Fig.~\ref{fig:Icons10Family}.
